%Text books : \cite{fraleigh}
%Module 1:
%Introduction to extension fields, algebraic extensions, Geometric Constructions Finite fields.
%(Part VI – Section 29, 31 – 31.1 to 31.18, 32, 33 of the text) (20 hours)
%Module 2:
%Unique factorization domains, Euclidean domains. Gaussian integers and multiplicative norms
%(Part IX – Sections 45,46 & 47 of the text) (20 hours)
%Module 3:
%Automorphism of fields, the isomorphism extension theorem , Splitting fields.
%(Part X – Sections 48 & 49, 50 of the text) (25 hours)
%Module 4:
%Separable extensions, Galois Theory, Illustrations of Galois Theory, Cyclotomic Extensions. (mention the insolvability of the quintic)
%( Sections 51, 53, 54, 55 - 55.1 to 55.6 of the text) (25 hours)

% ME010101 Abstract Algebra
%Module 1 - \cite{fraleigh} 11, 14, 16, 17
%Module 2 - \cite{fraleigh} 34, 36, 37
%Module 3 - \cite{fraleigh} 20, 21, 22, 23
%Module 4 - \cite{fraleigh} 24, 26, 27

%Advanced Abstract Algebra
%Module 1 - \cite{fraleigh} 29, 31, 32, 33
%Module 2 - \cite{fraleigh} 45, 46, 47
%Module 3 - \cite{fraleigh} 48, 49, 50
%Module 4 - \cite{fraleigh} 51, 53, 54, 55

%Missing - \cite{fraleigh} 1, 2, 3, 4, 5, 6, 7, 8, 9, 10,
%	12, 13, 15, 18, 19, 25, 28, 30, 35, 38, 39, 40, 41, 42, 43, 44

%Module 1
{\Large Module 1 Field Extensions}
\section{Extension Fields \S29}
\subsubsection*{Context}
\begin{itemize}
	\item Let $R$ be a commutative ring with unity.
		If $M$ is a maximal ideal in $R$, then $R/M$ is a field.
		\cite[\S27.9]{fraleigh}
	\item Let $F$ be a field.
		Every polynomial in $F[x]$ has a unique factorisation into irreducible polynomials except for order and unit.
		cite[\S27.27]{fraleigh}
	\item If $\alpha$ is a zero of $f(x) \in F[x]$, then $f(\alpha) = 0$.
		cite[\S22.10]{fraleigh}
	\item If $p(x)$ is irreducible over field $F$, then the principal ideal generated by $p(x)$, denoted by $\generator{p(x)}$ is a maximal ideal in $F[x]$.
		\cite[\S27.25]{fraleigh}
	\item Let $R$ be a ring with unity.
		And $N$ be an ideal of $R$ containing a unit.
		Then $N = R$.\cite[\S27.5]{fraleigh}
\end{itemize}

\begin{description}
	\item[Basic Goal] Let $F$ be a field and $f(x) \in F[x]$.
	Find a field $E$ such that\\
	$F$ is a subfield of $E$ and there exists a zero of $f(x)$ in $E$ ?
	\item[Extension Field] Let $F$ be a field.
	Field $E$ is an extension field of $F$ if $F$ is a subfield of $E$. \\
	Example : $\mathbb{Q} \le \mathbb{R} \le \mathbb{C}$
	\item[Tower of Fields] A diagrammatic representation emphasising the hierarchy of field extensions in which extension fields appears above their subfields.
\end{description}

\begin{theorem}[Kronecker]
	Let $F$ be field.
	And $f(x)$ be a non-constant polynomial in $F[x]$.
	Then there exists an extension field $E$ of $F$ and an $\alpha \in E$ such that $f(\alpha) = 0$.
\end{theorem}
\begin{proof}
	Let $f(x) \in F[x]$.
	Then $f(x)$ has a unique factorisation into irreducible polynomials in $F[x]$ (except for order and unit).
	Let $p(x)$ be an irreducible factor of $f(x)$.
	If $f(x)$ is irreducible over $F$, then $f(x) = cp(x)$.
	It is enough to construct an extension field $E$ containing both $F$ and $\alpha$ such that ${\color{red}p}(\alpha) = 0$.\\

	If $p(x)$ is irreducible over $F$, then $\generator{p(x)}$ is maximal ideal in $F[x]$.
	Therefore, $F[x]/\generator{p(x)}$ is a field, say $E$.\\

	Consider the function $\psi : F \to F[x]/\generator{p(x)}$ defined by $\psi(a) = a+\generator{p(x)}$.
	We claim that $\psi : F \to \psi[F]$ is a field isomorphism.
	$\psi$ is a canonical homomorphism with trivial kernel. Thus, $\psi$ is one-to-one.\\

	Let $a,b \in F$.
	And suppose $\psi(a) = \psi(b)$.
	It is enough to prove that $a = b$.
	By the definition of $\psi$, we have $a+\generator{p(x)} = b + \generator{p(x)} \implies a-b \in \generator{p(x)}$.
	Suppose $a \ne b$.
	Then $a-b \ne 0$ and $degree(a-b) = 0$.
	Then, $\generator{p(x)} = F[x]$ which is a contradiction since $\generator{p(x)}$ is maximal ideal.
	Therefore, $\psi$ is one-to-one.\\
	
	We have $p(x)$ is a factor of $f(x)$.
	Thus $p(\alpha) = 0 \implies f(\alpha) = 0$.
	Thus, it remains to prove that there exists $\alpha \in F[x]/\generator{p(x)}$ such that $p(\alpha) = 0$.\\

	Let $p(x) = a_0 + a_1x + a_2 x^2\cdots + a_n x^n$.
	Consider $\alpha = x + \generator{p(x)}$.
	Then $p(\alpha) = \phi_\alpha(p)$.
	Thus, $p(\alpha) = a_0 + a_1(x+\generator{p(x)}) + \cdots + a_n(x + \generator{p(x)})^n$.
	Thus, $p(\alpha) = (a_0+a_1x + a_n x^n) + \generator{p(x)} = p(x) + \generator{p(x)} = \generator{p(x)} = 0$.
	Therefore, $p(\alpha) = 0$ and $f(\alpha) = 0$.
\end{proof}

\begin{description}
	\item[algebraic over $F$] Let $F \le E$.
		An element $\alpha \in E$ is algebraic over a field $F$, if there exists $f(x) \in F[x]$ such that $f(\alpha) = 0$.
	\item[transcendental over $F$] Let $F \le E$.
		An element $\alpha \in E$ is transcendental over the field $F$, if it is not algebraic over $F$.
	\item[algebraic number] We have, $\mathbb{Q} \le \mathbb{C}$. A complex number $\alpha \in \mathbb{C}$ is algebraic if  it is algebraic over $\mathbb{Q}$.
		Example : $2,\sqrt{2},i$
	\item[transcendental number] A complex number $\alpha \in \mathbb{C}$ is transcendental if it is not an algebraic number.
		Example : $\pi,e$ (proof excluded)
\end{description}
\hrule \vspace{1em}
\textbf{Note 1} : A polynomial $f(x) \in F[x]$ is reducible/irreducible depending upon the choice of the field $F$.
For example : $x^2-2$ is irreducible over $\mathbb{Q}$, but is reducible over $\mathbb{R}$.

\textbf{Note 2} : An element $\alpha \in E$ is algebraic/transcendental depending on the choice of the field $F$.
For example : $\sqrt{2} \in \mathbb{C}$ is algebraic over $\mathbb{Q}$ since $x^2-2 \in \mathbb{Q}[x]$.
\hrule \vspace{1em}
\begin{theorem}
	Let $E$ be an extension field of $F$, and $\alpha \in E$.
	Let function $\phi_\alpha : F[x] \to E$ be an evaluation homomoprhism.
	Then $\alpha$ is transcendental  if and only if $\phi_\alpha$ is one-to-one.
\end{theorem}
\begin{proof}
	An element $\alpha \in E$ is transcendental if and only if $f(\alpha) \ne 0$ for any nonzero $f(x) \in F[x]$ where $f(\alpha) = \phi_\alpha(f)$.
	Thus, kernel of $\phi_\alpha$ is trivial.
	That is, $\ker(\phi_\alpha) = \{ 0 \}$.
	Therefore, $\phi_\alpha$ is one-to-one.
\end{proof}

\begin{theorem}
	Let $E$ be an extension field of $F$ and $\alpha \in E$ be algebraic over $F$.
	Then there exists a unique irreducible polynomial $p(x)$ with minimum degree in $F[x]$ and $p(\alpha) = 0$.
	If there exists a nonzero polynomial $f(x) \in F[x]$ with $f(\alpha) = 0$, then $p(x)$ divides $f(x)$.
\end{theorem}
\begin{proof}
	Consider evaluation homomorphism $\phi_\alpha : F[x] \to E$ defined by $\phi_\alpha(f) = f(\alpha)$.
	Then $\ker(\phi)$ is an ideal in $F[x]$.
	Since every ideal in $F[x]$ is principal, there exists $p(x) \in F[x]$ such that $\generator{p(x)} = \ker(\phi)$.
	And $f(\alpha) = 0 \implies f \in \ker(\phi) = \generator{p(x)}$.
	Thus, $p(x)$ divides $f(x)$.\\

	Suppose $p(x) = r(x)s(x)$.
	Then $p(\alpha) = r(\alpha)s(\alpha) = 0$.
	However, $E$ is a field and has no zero divisors.
	Thus, there exists a polynomial of lesser degree in $\generator{p(x)}$ which is a contradiction.
\end{proof}

\begin{description}
	\item[monic polynomial] A polynomial which has $1$ as the coefficient of highest power of $x$.
		For example : $x^3 - 3x \in \mathbb{Q}[x]$
	\item[$irr(\alpha,F)$] The unique monic, irreducible polynomial $p(x) \in F[x]$ such that $p(\alpha) = 0$.
		For example, $irr(\sqrt{3},\mathbb{Q}) = x^2-3$.
		And $\sqrt{3}$ is the \textbf{minimial} polynomial for $\sqrt{3}$ over $\mathbb{Q}$
	\item[$deg(\alpha,F)$] The degree of the unique monic, irreducible polynomial $p(x) \in F[x]$ such that $p(\alpha) = 0$.
		For example, $deg(\sqrt{3},\mathbb{Q}) = 2$.
	\item[simple extension] An extension field $E$ of field $F$ is a simple extension if $E = F(\alpha)$ for some $\alpha \in E$.
\end{description}

\begin{theorem}
	Let $E$ be a simple extension $F(\alpha)$ of field $F$ where $\alpha \in E$ is algebraic over $F$.
	Let $deg(\alpha,F) = n \ge 1$.
	Then any element $\beta \in E$ can be uniquely expressed in the form $\beta = b_0 + b_1\alpha + \cdots + b_{n-1}\alpha^{n-1}$ where $b_k \in F$.
\end{theorem}
\begin{proof}
	Consider the evaluation homomorphism $\phi_\alpha : F[x] \to E$ defined by $\phi_\alpha(f) = f(\alpha)$.
	Then $\phi_\alpha[F[x]] = F(\alpha)$.\\
	
	Let $irr(\alpha,F) = p(x) = x^n + a_{n-1}x^{n-1} + \cdots +a_1x+a_0$.
	Then, $p(\alpha) = 0$.
	Thus, 
\begin{equation}
	\alpha^n = -a_{n-1} \alpha^{n-1}-a_{n-2} \alpha^{n-2} - \cdots - a_1\alpha - a_0
\end{equation}
	Clearly, any higher power of $\alpha$ can be eliminated from $f(\alpha)$ as shown below,
	\begin{align*}
		\alpha^{n+1} = & \alpha \alpha^n = -a_{n-1} \alpha^n -a_{n-2} \alpha^{n-1} - \cdots - a_1\alpha^2 - a_0 \alpha \\ 
		 = & a_{n-1} \left( a_{n-1}\alpha^{n-1}+a_{n-2}\alpha^{n-2}+\cdots+a_1\alpha + a_0 \right)\\
		& - a_{n-2}\alpha^{n-1} - a_{n-3}\alpha^{n-2} - a_1\alpha^2 - a_0 \alpha
	\end{align*}

	Thus, in the representation of the element in $F(\alpha)$, the maximum degree of $\alpha$ is $deg(\alpha,F)-1$.
	Therefore, $\beta \in F(\alpha) \implies \beta = b_0 + b_1\alpha + b_2\alpha^2 + \cdots + b_{n-1}\alpha^{n-1}$.\\

	We can also show that this representation is unique for any $\beta \in F(\alpha)$.
	Suppose $\beta = b_0'+b_1'\alpha+b_2'\alpha^2+\cdots+b_{n-1}'\alpha^{n-1}$.
	Then $0 = (b_0 - b_0') + (b_1 - b_1')\alpha + \cdots + (b_{n-1} - b_{n-1}')\alpha^{n-1} = \phi_\alpha(g)$ where $g(x) = (b_0 - b_0') + (b_1 - b_1')x + \cdots + (b_{n-1} - b_{n-1}')x^{n-1}$.
	Clearly, degree of $g(x)$ is $deg(\alpha,F)-1$ which is less than the minimum degree for a non-zero irreducible polynomial for $\alpha$ over $F$.
	Thus $g(x) = 0$.
	In other words, $b_j = b_j',\ \forall j$ and representation for $\beta \in F(\alpha)$ is unique.
\end{proof}
\subsection{Exercises \S29}
\subsubsection{Irreducibility Conditions for Polynomials}
\begin{enumerate}
	\item Irreducibility over a finite field\\
		$x^2+1$ is irreducible in $\mathbb{Z}_3$ since for every $x \in \{ 0,1,2 \},\ x^2+1 \ne 0$.
\item Irreducibility in rational field : Eisentein's Criteria (\S23.15) \\
	Consider $f(x) = x^3+60x^2+30x+12$ since for $p=3$, $f(x)$ satisfies Eisentein's Criteria.
		And thus is $f(x)$ irreducible over $\mathbb{Q}$.\\
	Note that for $p = 2,5,7,\dots$ the Eisentein's Criteria is not satisfied.
\end{enumerate}
\subsubsection{Algebraic over a Field}
\begin{enumerate}
	\item $\sqrt{2}+\sqrt{3}$ is algebraic over $\mathbb{Q}$ \cite[Exercise 29.2]{fraleigh}
	\begin{align*}
		\alpha = & \sqrt{2} + \sqrt{3} \\
		\implies \alpha^2 = & 2 + 2\sqrt{6} + 3 =  5 + 2\sqrt{6}  \\
		\implies \alpha^2 - 5 =  & 2\sqrt{6} \\
		\implies  (\alpha^2-5)^2 = & 24 \\
		\implies \alpha^4 - 10\alpha^2 + 1 = & 0 \\
		\implies \phi_{\alpha}(x^4 - 10x^2 + 1) = & 0 
	\end{align*}
		We have, $irr(\sqrt{2}+\sqrt{3},\mathbb{Q}) = x^{\textcolor{blue}{4}}-10x^2+1$ and $deg(\sqrt{2}+\sqrt{3},\mathbb{Q}) = \textcolor{blue}{4}$.
	\item $\pi,e$ are transcendental numbers. (proof excluded)\\
		However, $\pi$ is algebraic over $\mathbb{Q}(\pi)$ since $x-\pi \in \mathbb{Q}(\pi)[x]$.
		
	\item Consider $\alpha = \pi^2$ and $F = \mathbb{Q}(\pi^3)$. \cite[Exercise 29.16]{fraleigh}
	\begin{align*}
		\alpha^3 = & \pi^6 = (\pi^3)^2 \\
		\alpha^3-(\pi^3)^2 = & 0 \\
		\implies \phi_\alpha(x^3-(\pi^3)^2) = & 0 
	\end{align*}
	Thus, $irr(\pi^2,\mathbb{Q}(\pi^3)) = x^{\textcolor{blue}{3}}-(\pi^3)^2$ and $deg(\pi^2,\mathbb{Q}(\pi^3)) = \textcolor{blue}{3}$.\\ 
		Note that $x^3-(\pi^3)^2 \in \textcolor{blue}{\mathbb{Q}(\pi^3)[x]}$ since $\pi^3 \in \mathbb{Q}(\pi^3) \implies -(\pi^3)^2 \in \mathbb{Q}(\pi^3)$.
		However, $x^3-(\pi^3)^2 \notin \textcolor{blue}{\mathbb{Q}[x]}$.
\end{enumerate}
\subsubsection{Factorisation over Extended Field}
\begin{enumerate}
	\item Factorisation over Finite Extension of Finite Field \cite[Exercise 29.25]{fraleigh}\\
		Let $\alpha$ be a zero of $f(x) = x^3+x^2+1 \in \mathbb{Z}_2[x]$.
		Clearly, $f(x)$ is irreducible over $\mathbb{Z}_2$.
		And $x-\alpha$ is a factor of $f(x)$ in $\mathbb{Z}_2(\alpha)$. We have, $f(x) = (x-a)g(x)$

		\[\text{By long division, } g(x) = \frac{x^3+x^2+1}{x-\alpha} = x^2+(1+\alpha)x+(\alpha+\alpha^2)\]
		Therefore, $x^3+x^2+1 = (x-\alpha)[x^2+(1+\alpha)x+\alpha(1+\alpha)]$.\\

		The elements of $\mathbb{Z}_2(\alpha)$ are of the form $a_0+a_1\alpha+a_2\alpha^2$ where $a_0,a_1,a_2 \in \{0,1\}$.
		Also we have, $\alpha$ is a zero of $x^3+x^2+1$.
		Thus, $\alpha^3 = \alpha^2+1$.\\

		In order to find a zero of $g(x)$ it is sufficient to evaluate $g(x)$ for all the eight elements $ 0, 1, \alpha, (1+\alpha), \alpha^2, (1+\alpha^2),(\alpha+\alpha^2), (1+\alpha+\alpha^2) \in \mathbb{Z}_2(\alpha)$.
		
		Clearly, $g(1) = \alpha^2+2\alpha+2 = \alpha^2$.
		And $g(\alpha) = \alpha^2 + 2\alpha(1+\alpha) = \alpha^2$.
		However, $g(\alpha^2) = \alpha^4+\alpha^3+2\alpha^2+\alpha = \alpha(\alpha^2+1)+(\alpha^2+1) + 0\alpha^2 + \alpha = \alpha^3 + \alpha^2 + 2\alpha + 1 = \alpha^3+\alpha^2+1 = 0$.
		Thus, $\alpha^2$ is a zero of $g(x)$ and $g(x) = (x-\alpha^2)h(x)$.
		\[\text{By long division, } h(x) = \frac{x^2+(1+\alpha)x+(\alpha+\alpha^2)}{x-\alpha^2} = x+(1+\alpha+\alpha^2)\]
		Therefore, we have the following linear factoriation for $f(x)$,\\ $f(x) = (x-\alpha)(x-\alpha^2)(x-1-\alpha-\alpha^2) = (x+\alpha)(x+\alpha^2)(x+1+\alpha+\alpha^2)$ since $-\alpha = 0-\alpha = 2\alpha-\alpha = \alpha$ in $\mathbb{Z}_2$.\\

	Note : Students should be able to perform long division of polynomials over extended fields.
\end{enumerate}

\section{Algebraic Extensions \S31}
\begin{description}
	\item[$(G : H)$] is the number of $H$-left cosets in $G$.
	\item[algebraic extension] A extension field $E$ of a field $F$ is algebraic if every element in $E$ is algebraic over $F$.\\
		For example, $\mathbb{C}$ is algebraic over $\mathbb{R}$.
		But, $\mathbb{R}$ is not algebraic over $\mathbb{Q}$.
	\item[finite extension] A extension field $E$ of field $F$ is a finite extension if $E$ is a finite dimensional vector space over $F$.
		And $[E:F]$ is the \textbf{dimension of the vector space} $E$ over $F$.
		Again, $[E:F]$ is the \textbf{degree of the finite extension} $E$ over $F$.\\
		For example, $\mathbb{C}$ is a finite extension of degree $2$ over $\mathbb{R}$, $[\mathbb{C} : \mathbb{R}] = 2$. But, $\mathbb{R}$ is not a finite extension of $\mathbb{Q}$ and $[\mathbb{R} : \mathbb{Q}]$ is infinite.
\end{description}

\begin{theorem}
	Every finite field extensions is an algebraic extension.
\end{theorem}
\begin{proof}
	Let $E$ be a fintie extension of degree $n$ over $F$.
	Then $[E:F] = n$.
	Suppose $\alpha \in E$.
	Clearly, $\{1,\alpha,\alpha^2,\cdots,\alpha^n \}$ is set of $n+1$ vectors from the vector space $E$ over $F$.
	We know that in a vector space of dimension $n$, any set having $n+1$ vector is linearly dependant.
	In other words, there exits scalars $c_0,c_1,\cdots,c_n \in F$ (not all zero) such that $c_0+c_1\alpha+c_2\alpha^2+\cdots+c_n\alpha^n = 0$.\\

	Clearly, $f(x) = c_0 + c_1x + c_2x^2 + \cdots +c_nx^n$ is a polynomial in $F[x]$ such that $\phi_\alpha(f) = f(\alpha) = 0$.
	Since $\alpha \in E$ is arbitrary, every element in $E$ is algebraic over $F$.
\end{proof}

\begin{theorem}
	If $E$ is a finite extension of $F$ and $K$ is a finite extension of $E$.
	Then $K$ is a finite extension of $F$.
	And $[K:F] = [K:E][E:F]$.
\end{theorem}
\begin{proof}
	Let $[E:F] = n$ and $[K:E] = m$.
	Let $\{ \alpha_1,\alpha_2,\cdots,\alpha_n \}$ be basis for vector space $E(F)$ and let $\{ \beta_1,\beta_2,\cdots,\beta_m\}$ be basis for vector space $K(E)$.
	We claim that $\{\alpha_i\beta_j : 1 \le i \le n,\ 1 \le j \le m \}$ is a basis for the vector space $K(F)$.\\

	Let $\gamma \in K$.
	Then we have $b_1,b_2,\cdots,b_m \in E$ such that $\gamma = b_1\beta_1+b_2\beta_2+\cdots+b_m\beta_m$.
	Again, for each $b_j \in E$, we have $a_{ij} \in F$ such that $b_j = a_{1j}\alpha_1+a_{2j}\alpha_2+\cdots+a_{nj}\alpha_n$.
	Therefore, 
	\[\gamma = \sum_{i=1}^n \sum_{j=1}^m a_{ij} \alpha_i \beta_j\]

	That is, $\{ \alpha_i \beta_j : i =1,2,\cdots,n,\ j=1,2,\cdots,m \}$ spans $K$.
	It remains to prove that $\{\alpha_i \beta_j \}$ is linearly independent.
	Suppose it is linearly dependent.
	Then there exists scalars $c_{i,j} \in F$ (not all zero) such that
	\[\sum_{i=1}^n \sum_{j=1}^m c_{i,j} \alpha_i \beta_j  = \sum_{j=1}^m \left( \sum_{i=1}^n c_{i,j} \alpha_i \right) \beta_j  = 0\]
	
	Let $\sum_{i=1}^n c_{i,j}\alpha_i = b_j$.
	We know that, $\{ \beta_j : j = 1,2,\cdots,m \}$ is linearly independent.
	Thus, $\sum_j b_j \beta_j = 0 \implies b_j = 0,\ \forall j$.\\
	

	Again $b_j = 0 \implies \sum_{i = 0}^n c_{i,j}\alpha_i = 0$.
	Once again, $\{ \alpha_i : i = 1,2,\cdots,n \}$ is linear independent.
	Thus, $c_{i,j} = 0,\ \forall i,j$.
	Thus, $\{ \alpha_i \beta_j \}$ is linearly independent.
	Therefore, $\{ \alpha_i \beta_j \}$ is a basis for the vector space $K(F)$.
	And $[K : F] = |\{\alpha_i \beta_j : i =1,2,\cdots,n \text{ and } j=1,2,\cdots,m\}|= mn$.
\end{proof}

\begin{corollary}
	Let $F_i$ be fields and $F_{i+1}$ are finite extensions of $F_i$s for $i = 1,2,\cdots,r$.
	Then $[F_r : F_1] = [F_r : F_{r-1}][F_{r-1}:F_{r-2}]\cdots[F_2:F_1]$.
\end{corollary}
\begin{proof}
	We have, $F_3$ is a finite extension of $F_1$ and 
	\begin{equation}
		[F_3:F_1] = [F_3:F_2][F_2:F_1]
	\end{equation}
	Suppose $F_k$ is a finite extension of $F_1$ and 
	\begin{equation}
		[F_k : F_1] = [F_k:F_{k-1}][F_{k-1}:F_{k-2}] \cdots [F_2:F_1]
	\end{equation}
	\begin{align*}
		[F_{k+1}:F_1] = & [F_{k+1} : F_k][F_k : F_1] \text{ since } F_k \text{ is a finite extension of } F_1\\
		= & [F_{k+1}:F_k][F_k:F_{k-1}][F_{k-1}:F_{k-2}] \cdots [F_2:F_1]
	\end{align*}
\end{proof}

\begin{corollary}
	If $E$ is an extension field of $F$ and $\alpha \in E$ is algebraic over $F$ and $\beta \in F(\alpha)$, then $deg(\beta,F)$ divides $deg(\alpha,F)$.
\end{corollary}
\begin{proof}
	We have, $\deg(\alpha,F) = [F(\alpha) : F]$ and $\deg(\beta,F) = [F(\beta):F]$.
	Also given that $\beta \in F(\alpha) \implies F(\beta) \le F(\alpha)$.
	Clearly, $F \le F(\beta) \le F(\alpha)$.
	Therefore, $[F(\alpha) : F] = [F(\alpha):F(\beta)][F(\beta):F]$.
	And $[F(\alpha):F(\beta)] = [F(\alpha):F]/[F(\beta):F]$.
	Clearly, $[F(\beta):F]$ divides $[F(\alpha):F]$.
\end{proof}

\begin{theorem}[algebraic closure]
	Let $E$ be an extension field of $F$.
	Then $\bar{F}_E = \{ \alpha \in E : \alpha \text{ is algebraic over } E \}$ is a subfield of $E$.
\end{theorem}
\begin{proof}
	Let $\alpha,\beta \in \bar{F}_E$.
	Then $\alpha,\beta \in E$ are algebraic over $F$.
	And $F(\alpha,\beta)$ is a finite extension field of $F$.
	Thus every element in $F(\alpha,\beta)$ are algebraic over $F$.
	Thus, $\alpha+\beta, \alpha\beta,\alpha-\beta,\alpha/\beta \in \bar{F}_E$.
	Therefore, $\bar{F}_E$ is a subfield of $E$.
\end{proof}

\begin{corollary}
	The set of all algebraic numbers forms a field.
\end{corollary}
\begin{proof}
	Let $\alpha$ be an algebraic number.
	Then $\alpha \in \mathbb{C}$ and $\alpha$ is algebraic over $\mathbb{Q}$.
	Clearly, the set of all algebraic numbers, $\bar{\mathbb{Q}}_\mathbb{C}$ is a subfield of $\mathbb{C}$.
\end{proof}

\begin{description}
	\item[algebraic closure] Let $F$ be a field and $E$ be an extension field of $F$.
		Then the (smallest) field containing all elements of $E$ which are algebraic over $F$ is the algebraic closure $\bar{F}_E$ of $F$ in $E$.
	\item[algebraically closed] Let $F$ be a field.
		$F$ is algebraically closed if every non-constant polynomial in $F[x]$ has a zero in $F[x]$.
		
\end{description}

\textbf{Note : } Let $F$ be algebraically closed.
Then every irreducible polynomial in $F[x]$ are linear since every non-constant polynomial has a linear factor.

\begin{theorem}
	A field $F$ is algebraically closed if and only if every non-constant polynomial $f(x)$ can be factorised in $F[x]$ into linear factors.
\end{theorem}
\begin{proof}
	Let $F$ be algebraically closed and $f(x)$ be a non-constant polynomial in $F[x]$.
	Then $f(x)$ has a zero $\alpha \in F$.
	Then $x-\alpha$ is a factor of $f(x)$.
	That is, $f(x) = (x-\alpha)g(x)$.
	If $g(x) \in F[x]$ is non-constant, then it has a zero in $F$.
	Continuing like this, $f(x)$ can be factorised in $F[x]$ into linear factors.\\

	Suppose every non-constant polynomial in $F[x]$ can be factorised into linear factors.
	Let $f(x)$ be a non-constant polynomial in $F[x]$.
	Then $f(x)$ has a linear factor $(ax+b) \in F[x]$.
	Clearly, $-b/a$ is a zero of $f(x)$.
\end{proof}

\begin{theorem}
	Algebraically closed field has no proper algebraic extensions.
\end{theorem}
\begin{proof}
	Let $E$ be an algebraic extension field of $F$.
	Then if $\alpha \in E$, we have $irr(\alpha,F) = (x-\alpha)$ since $F$ is algebraically closed, every irreducible polynomial in $F[x]$ are linear.
	Thus $\alpha \in F$.
	Since $\alpha \in E$ is arbitrary, $F = E$.
\end{proof}

\begin{theorem}[Fundamental Theorem of Algebra]
	$\mathbb{C}$ is algebraically closed.
\end{theorem}
\begin{proof}
	Let $f(z) \in \mathbb{C}[z]$.
	Suppose $f(z)$ has no zeroes in $\mathbb{C}$.
	Then $1/f(z)$ is an entire function and as $|z| \to \infty$, $|f(z)| \to \infty$.
	Thus, $\lim_{|z|\to\infty} \frac{1}{|f(z)|} = 0$.
	And $1/f(z)$ is bounded.\\
	
	By Liouville's theorem, every bounded entire function is constant.
	Therefore, $1/f(z)$ is constant and $f(z)$ is also constant.
	Thus, every non-constant polynomial function in $\mathbb{C}[z]$ has a zero in $\mathbb{C}$.
\end{proof}

\begin{description}
	\item[POSET] Partial Ordered Set - A set together with partial order (reflexive, antisymmetric, transitive relation).\\
		
	For example $(\mathbb{R},<)$, the set of all real numbers together with less than relation is a poset.
		However, in a poset it is not necessary that two arbitrary elements are comparable.
		$(\mathbb{C},R)$ defined by $aRb$ if $\Re(a) = \Re(b)$ and $Im(a) < Im(b)$ is a poset in which $2+3i$ and $3+3i$ are not comparable.
	\item[chain] A subset of a poset in which any two elements are comparable.
		That is, $x,y \in T \implies x < y \text{ OR } y < x$.\\

	For example, For above defined poset $(\mathbb{C},R)$, $T = \{ 2+ib \in \mathbb{C} : b \in \mathbb{R} \}$ is a chain in $\mathbb{C}$.
\end{description}
\begin{lemma}[Zorn]
	If every chain in a poset $S$ has an upper bound.
	Then $S$ has at least one maximal element in it.
\end{lemma}
\begin{proof}
	Not required ( I think, there is no proof.
	We just take it as an axiom - always true !.
	If it is not true for a collection then it is not a set !! )
\end{proof}
\begin{theorem}[Existence of Algebraic Closure]
	Every field $F$ has an algebraic closure $\bar{F}$.
\end{theorem}
\begin{proof}
	Not required (as per syllabus)
\end{proof}
\subsection{Exercise \S31}
\begin{enumerate}
	\item
\end{enumerate}

\section{Geometric Constructions \S32}
\subsection{Basic Constructions}
\subsubsection{Finding Midpoint of a line}
	Let $OA$ be a line.
	The line passing through the intersection of circles with center $O$ and $A$ with diameter greater than the length of the line gives a perpendicular line through its mid point (say, perpendicular bisection).

\subsubsection{Drawing Perpendicular line through a point}
	Let $OA$ be a line and $B$ be a point on that line.
	Find points $P,Q$ on $OA$ which are equidistant from $B$.
	Then the perpendicular bisection of $PQ$ is a line perpendicular to $OA$ through $B$.
\subsubsection{Drawing Parallel Line} 
	Let $OA$ be a line.
	Then the perpendicular line segment of any perpendicular line segment is a line segment parallel to $OA$.
\subsection{Constructible Numbers}
\begin{description}
	\item[Constructible Number] A real number $\alpha$ is constructible if you can draw a line of length $|\alpha|$, given a line of unit length, in finite steps using straightedge and compass.
\end{description}
\begin{theorem}
	Let $\alpha,\beta$ be constructible real numbers.
	Then $\alpha + \beta$, $\alpha-\beta$, $\alpha\beta$, $\alpha/\beta$ ($\beta \ne 0$) are also constructible.
\end{theorem}
\begin{proof}
\begin{description}
	\item[$\alpha+\beta$] Draw a line $OA$ of length $|\alpha|$ and extend that line using straight edge $OE$.
		And draw the line $AB$ of length $|\beta|$ on that extended line, at an point $A$ of the former line extending it.
		Then $OB$ is a line of length $|\alpha| + |\beta|$.
\begin{center}
\begin{tikzpicture}
	\draw[red] (0,0) -- (5,0);
	\draw (0,0) -- (3,0);
	\draw (0,-0.3) node{$O$};
	\draw (3,-0.3) node{$A$};
	\draw (5,-0.3) node{$B$};
\end{tikzpicture}
\end{center}
	\item[$\alpha-\beta$] Draw a line $OA$ of length $|\alpha|$ and extend that line using straight edge $OE$.
		And draw the line $AB$ of length $|\beta|$ on that extended line, at an end point $A$ of former line, but in the opposite direction of extension( towards $O$).
		Then the line $OB$ is of length $|\alpha|-|\beta|$.
\begin{center}
\begin{tikzpicture}
	\draw[blue] (0,0) -- (3,0);
	\draw[red] (0,0) -- (1,0);
	\draw (0,-0.3) node{$O$};
	\draw (3,-0.3) node{$A$};
	\draw (1,-0.3) node{$B$};
\end{tikzpicture}
\end{center}
	\item[$\alpha\beta$] Draw two lines $OA$ and $OB$ of length $|\alpha|$ and $|\beta|$ respectively (with a common end point $O$).
		Now draw the line of unit length $OP$ along the line $OB$.
		Construct triangle $OAP$.
		Draw the line $BQ$ parallel to the line $PA$ through $B$ such that $OQ$ and $OA$ are colinear.
		Now we have two similar triangles $OPA$ and $OBQ$.
		Then, the line $OQ$ of length $\| \alpha \beta \|$.
\begin{center}
\begin{tikzpicture}
	\draw[red] (0,0) -- (6,0);
	\draw (0,0) -- (3,0);
	\draw[blue] (0,0) -- (2.5,2);
	\draw (0,0) -- (1.25,1);
	\draw (2.5,2) -- (6,0);
	\draw (1.25,1) -- (3,0);
	\draw (0,-0.3) node{$O$};
	\draw (3,-0.3) node{$A$};
	\draw (1.25,1.3) node{$P$};
	\draw (2.5,2.3) node{$B$};
	\draw (6,-0.3) node{$Q$};
\end{tikzpicture}
\end{center}
	\item[$\alpha/\beta$] Draw two lines $OA$ and $OB$ of length $\| \alpha \|$ and $\| \beta \|$, with a common end point $O$.
		Draw a line of unit length $OP$ along the line $OB$.
		Now construct triangle $OBA$.
		Draw line $PQ$ parallel to $BA$ so that $OQ$ and $OA$ are colinear.
		Now the triangles $OAB$ and $OQP$ are similar.
		And the line $OQ$ has length $\| \alpha/\beta \|$.
\begin{center}
\begin{tikzpicture}
	\draw[red] (0,0) -- (6,0);
	\draw (0,0) -- (3,0);
	\draw[blue] (0,0) -- (1.5,2);
	\draw (0,0) -- (0.75,1);
	\draw (1.5,2) -- (6,0);
	\draw (0.75,1) -- (3,0);
	\draw (0,-0.3) node{$O$};
	\draw (3,-0.3) node{$Q$};
	\draw (0.60,1.06) node{$P$};
	\draw (1.5,2.3) node{$B$};
	\draw (6,-0.3) node{$A$};
\end{tikzpicture}
\end{center}
\end{description}
\end{proof}

\begin{corollary}
	The set of all constructible real numbers forms a subfield of the field of real numbers.
\end{corollary}
\begin{proof}
	The set of all constructible real numbers say $H$, contains both $0$ and $1$.
	since the line of length zero is trivial and line of unit length is provided.
	And we have, $\forall \alpha,\beta \in H,\ \alpha+\beta,\alpha-\beta,\alpha\beta,\alpha/\beta \in H$.
	Since $\alpha - \beta \in H$, $0-\beta = -\beta$ which is the additive inverse of $\beta$.
	And $1/\beta = \beta^{-1}$ is the multiplicative inverse of $\beta$.
	Thus, the set of all constructible numbers is a subfield of $\mathbb{R}$.
\end{proof}

\begin{theorem}
	The field of $F$ of constructible numbers consists {\color{blue}precisely} of all real numbers that we can obtain from $\mathbb{Q}$ by taking square root of positive numbers a finite number of times and applying a finite number of field operations.
\end{theorem}
\begin{proof}
	The constructible numbers are closed under field operations and forms a subfield $H$ of real numbers.
	We have, $\mathbb{Q}$ is the prime field of $\mathbb{R}$.
	That is, every subfield of $\mathbb{R}$ contains $\mathbb{Q}$.
	Thus, the subfield $H$ of constructible numbers contains $\mathbb{Q}$.
	That is, all the rational numbers are constructible.
	Therefore, it remains to prove that if $\alpha > 0$ is constructible then $\sqrt{\alpha}$ is also constructible.
\begin{center}
\begin{tikzpicture}
	\draw[blue] (0,0) -- (4,0);
	\draw (0,0) -- (-1,0);
	\draw[red] (0,0) -- (0,2);
	\draw (0,-0.3) node{$O$};
	\draw (4.2,0) node{$A$};
	\draw (-1.3,0) node{$P$};
	\draw (0,2.3) node{$Q$};
	\draw[dotted] (1.5,0) -- (1.5,2.5);
	\begin{scope}
		\clip (-1,0) rectangle (4,2.5);
		\draw (1.5,0) circle (2.5cm);
	\end{scope}
	\draw (4,0) -- (0,2);
	\draw (-1,0) -- (0,2);
\end{tikzpicture}
\end{center}

	Let $OA$ and $OP$ be colinear lines such that $OA$ be a line of length $\| \alpha \|$ and $OP$ be a line of unit length.
	Find the mid point of $PA$ and draw a circle of diameter $PA$.
	Then the length of the perpendicular $OQ$ from $PA$ to the circle is of length $\| \sqrt{\alpha} \|$ since $\Delta OAQ$ and $\Delta OQP$ are similar triangles.\\


	Therefore, real numbers obtained from rational numbers through finite number of additions/subtractions, multplications/divisions, and square root are constructible.
\end{proof}
\hrule\vspace{1em}
\textbf{Note : } For example $\sqrt[4]{5\sqrt[8]{3}-2}$ is constructible, but $\sqrt[6]{2}$ and $\pi$ are not constructible.
We skip the proof that a real number which can't be obtained from rationals by a finite number of these operations is not constructible.
And assume that these three operations define the entire field of constructible numbers.
\hrule\vspace{1em}
\begin{corollary}
	Let $\gamma$ be constructible number which is not rational.
	Then there exists a sequence of real numbers $\alpha_1,\alpha_2,\dots,\alpha_n = \gamma$ such that for every $i = 2,\dots,n$, the extension field $\mathbb{Q}(\alpha_1,\alpha_2,\dots,\alpha_i)$ is an extension of $\mathbb{Q}(\alpha_1,\alpha_2,\dots,\alpha_{i-1})$ of degree two.\\

	In other words, for any constructible number $\gamma$, $[\mathbb{Q}(\gamma) : \mathbb{Q}] = 2^n$ for some positive integer $n$.
\end{corollary}
\begin{proof}
	Let $\gamma$ be a constructible number which can be obtained from rationals by $n$ square root operations and a finite number of field operations.
	Then, we have a sequence of constructible numbers $\alpha_1, \alpha_2,\dots, \alpha_n$ such that $[\mathbb{Q}(\alpha_1,\alpha_2,\dots,\alpha_i) : \mathbb{Q}(\alpha_1,\alpha_2,\dots,\alpha_{i-1})] = 2$.
	Therefore, $[\mathbb{Q}(\gamma) : \mathbb{Q}] = 2^n$.
\end{proof}
\hrule\vspace{1em}
	For example, $\gamma = \sqrt[4]{5\sqrt[8]{3}-2}$.
	Then $\alpha_1 = \sqrt{3}$, $\alpha_2 = \sqrt[4]{3}$, $\alpha_3= \sqrt[8]{3}$, $\alpha_4 = \sqrt{5\sqrt[8]{3}-2}$ and $\alpha_5 = \gamma$.
	Clearly, the geometric construction of $\gamma$ contains five instances of square root operation.
\hrule\vspace{1em}
\subsection{Impossible Problems from Ancient Times}
\subsubsection{Doubling the cube}
\begin{theorem}
	There exists a cube such that it is impossible to construct the side of the cube with double the volume.
\end{theorem}
\begin{proof}
	Suppose the cube is of unit side.
	Then the side of the cube with double the volume is $\gamma = \sqrt[3]{2}$.
	And $irr(\gamma,\mathbb{Q}) = x^3-2$ and $[\mathbb{Q}(\sqrt[3]{2}:\mathbb{Q}] = 3 \ne 2^n$.
	Therefore, $\gamma$ is not constructible.
\end{proof}
\subsubsection{Squaring the circle}
\begin{theorem}
	There exists a circle such that it is impossible to construct the side of the square with the same area.
\end{theorem}
\begin{proof}
	Suppose the circle of is of unit radius.
	Then area of the circle is $2\pi$.
	And the side of the square with same area is $\sqrt{2\pi}$.
	Since $\pi$ is transcendental, $\pi$,$\sqrt{\pi}$ and $\sqrt{2\pi}$ are not constructible.
\end{proof}
\subsubsection{Trisecting an angle}
\begin{theorem}
	There exists an angle which can be trisected.
\end{theorem}
\begin{proof}
	We have $\cos 3\theta = 4\cos^3 \theta - 3\cos \theta$.
	Consider $\theta = 20^\circ$.
	Then $\gamma = \cos \theta$ is a root of the irreducible polynomial $4x^3-3x-0.5$.
	That is, $\gamma$ is a root of the monic irreducible polynomial $x^3-\frac{3}{4}x-\frac{1}{8}$ of degree $3$.
	Thus, $\gamma$ is not constructible, since $[\mathbb{Q}(\gamma) : \mathbb{Q}] = 3 \ne 2^n$.
\end{proof}
\subsection{Exercise \S32}
\begin{enumerate}
	\item
\end{enumerate}

\section{Finite Fields \S33}
\subsection{Structure of a Finite Field}
\begin{theorem}
	Let $E$ be a finite extension of degree $n$ over a finite field $F$.
	If $F$ has $q$ elements, then $E$ has $q^n$ elements.
\end{theorem}
\begin{proof}
	We have, extension field $E$ is an $n$-dimensional vector space over the field $F$.
	Let $\{ \alpha_1, \alpha_2,\dots, \alpha_n \}$ be a basis of the vector space $E$ over $F$.
	Then every elements of $E$ can be uniquely written as linear combination of basis vectors.
\begin{equation*}
 	\forall \beta \in E,\ \beta = b_1 \alpha_1 + b_2 \alpha_2 + \dots + b_n \alpha_n
\end{equation*}
	Suppose $\beta \in E$ has two distinct linear combinations.
	Then, the vectors $\{ \alpha_1, \alpha_2,\dots,\alpha_n\}$ are not linearly independent, which is a contraditciton.\\
	
	Since the representation is unique and $F$ has $q$ elements, there are $q^n$ distinct linear combinations possible.
	Therefore, $E$ has $q^n$ elements.
\end{proof}

\begin{corollary}
	If $E$ is a finite field of characteristic $p$.
	Then $F$ contains exactly $p^n$ elements for some integer $n$.
\end{corollary}
\begin{proof}
	We have, $E$ is a finite field of characteristic $p$.
	Thus, $\mathbb{Z}_p$ is the prime subfield of $E$.
	And $E$ is a finite extension of $\mathbb{Z}_p$.
	Thus, $E$ is a finite dimensional vector space over $\mathbb{Z}_p$.
	Let $n$ be the dimension of $E$ over $\mathbb{Z}_p$.
	And $\mathbb{Z}_p$ has $p$ elements.
	Therefore, $E$ has $p^n$ elements.
\end{proof}

\begin{theorem}
	Let $E$ be a field of $p^n$ elements contained in the algebraic closure $\overline{\mathbb{Z}_p}$ of $\mathbb{Z}_p$.
	Then the elements of $E$ are precisely the zeroes of the polynomial $x^{p^n}-x \in \mathbb{Z}_p[x]$.
\end{theorem}
\begin{proof}
	We have $E^\ast$ is a multiplicative group of non-zero elements in $E$.
	And $E^\ast$ has $p^n-1$ elements.
	Thus, order of any element $\alpha \in E^\ast$ should divide $p^n-1$.
	In other words, if $\alpha \in E^\ast$, then $\alpha^{p^n-1} = 1$.
	Clearly, $\alpha^{p^n} - \alpha = 0$, $\forall \alpha \in E$.
	However, $x^{p^n}$ can have atmost $p^n$ zeroes in $\overline{\mathbb{Z}_p}$.
	Thus, $E$ is precisely the set of all zeroes of $x^{p^n}-x \in \overline{\mathbb{Z}_p}$.
\end{proof}

%\begin{enumerate}[label=Note \arabic*]
%	\item The algebraic closure of $\mathbb{Z}_p$ contains zeroes of every polynomial of the form $x^{p^n}-x$ where $p$ is a prime and $n$ is an integer. Thus, algebraic closures are infinite fields. Remember : $\mathfrak{R}1$
%	\item $\overline{\mathbb{Z}_2}$ has two distinct square roots of unity. And the complex field contains only one of them !
%\end{enumerate}

\begin{description}
	\item[$n$th Root of Unity] $\alpha$ is an $n$th root of unity if $\alpha^n = 1$.
		ie, $\alpha = \sqrt[n]{1}$
	\item[Primitive $n$th Root of Unity] $\alpha$ is a primitive $n$th root of unity if $n$ is the smallest positive integer such that $\alpha^n = 1$.\\
		That is, $\alpha^n = 1$ and $\forall m \in \mathbb{N},\ m < n \implies \alpha^m \ne 1$
\end{description}

\begin{theorem}
	The multiplicative group of non-zero elements of a finite field $F$ is cyclic.
\end{theorem}
\begin{proof}
	Refer : \cite[Theorem 23.6]{fraleigh}
\end{proof}
\begin{corollary}
	Finite extension of finite fields are simple extensions.
\end{corollary}
\begin{proof}
	Let $E$ be a finite extension field of the finite field $F$.
	Then the multiplicative group of non-zero elements $E^\ast$ is cyclic.
	Let $\alpha$ be a generator of the cyclic group $E^\ast$.
	Then, $E = F(\alpha)$.
\end{proof}

\subsection{Galois Field $GF(p^n)$}
\begin{lemma}
	If $F$ is a field of prime characteristic $p$ with algebraic closure $\overline{F}$, then $x^{p^n}-x$ has $p^n$ distinct zeroes in $\overline{F}$.
\end{lemma}
\begin{proof}
	We have, $\overline{F}$ is algebraically closed.
	And $x^{p^n}-x \in \overline{F}[x]$.
	Thus, $x^{p^n}-x$ can be factorised into $p^n$ linear components.
	It remains to prove that these factors are distinct.\\

	Clearly, $0$ is a zero of multiplicity $1$, since $x^{p^n}-x = x (x^{p^n-1}-1)$.
	Let $\alpha \ne 0$ be a zero of $x^{p^n}-x$.
	Then $\alpha$ is a zero of $x^{p^n-1}-1$.
	ie, $\alpha^{p^n-1}  = 1$.
	\begin{align*}
		(x-\alpha)g(x) = & x^{p^n-1}-1 \\
		g(x) = & \frac{x^{p^n-1}-1}{x-\alpha}
		\intertext{By long division, we get}
		g(x) = & x^{p^n-2} + \alpha x^{p^n-3} + \alpha^2 x^{p^n-4} + \dots + \alpha^{p^n-3} x + \alpha^{p^n-2} \\
		g(\alpha) = & (p^n-1)\alpha^{p^n-2} \\
		= &(p^n-1)\frac{\alpha^{p^n-1}}{\alpha} \\
		= & p^n \frac{1}{\alpha} - \frac{1}{\alpha}\\
		= & -\frac{1}{\alpha} \ne 0
	\end{align*}
	Thus, every zero of $x^{p^n-1}-x$ is of multiplicity $1$.
\end{proof}

\begin{lemma}
	If $F$ is a field of prime characteristic $p$, then $(\alpha+\beta)^{p^n} = \alpha^{p^n} + \beta^{p^n}$.
\end{lemma}
\begin{proof}
	Since $F$ is a field of characteristic $p$, for every $\alpha \in F$, $p\alpha = 0$.
	\begin{align*}
		\intertext{ For $n=1$, we have }
		(\alpha+\beta)^p = & \alpha^p + p \alpha^{p-1}\beta+ \frac{p(p-1)}{2} \alpha^{p-2} \beta + \dots + p \alpha \beta^{p-1} + \beta^p \\
		= &  \alpha^p + 0 \alpha^{p-1}\beta+ 0 \alpha^{p-2} \beta + \dots + 0 \alpha \beta^{p-1} + \beta^p \\
		= & \alpha^p + \beta^p
	\end{align*}
	\begin{align*}
		\intertext{Suppose $(\alpha+\beta)^{p^{n-1}} = \alpha^{p^{n-1}} + \beta^{p^{n-1}}$, then} 
		(\alpha+\beta)^{p^n} = & \left[ (\alpha+\beta)^{p^{n-1}} \right]^p \\
		= & \left[ \alpha^{p^{n-1}} + \beta^{p^{n-1}} \right]^p \\
		= & \alpha^{p^n} + \beta^{p^n}
	\end{align*}
	Therefore, by mathematical induction the result is true.
\end{proof}

\begin{theorem}[Existence of Galois Field]
	For every prime power $p^n$, a finite field of $p^n$ elements exists.
\end{theorem}
{\color{blue} Hint : $\alpha^{p^n} = \alpha \iff \alpha^{p^n} - \alpha = 0 \iff \alpha$ is a zero of $x^{p^n} - x$}
\begin{proof}
	Consider the algebraic closure $\overline{\mathbb{Z}_p}$ of $\mathbb{Z}_p$.
	Let $K$ be a subset of $\overline{\mathbb{Z}_p}$ containing all zeroes of $x^{p^n}-x \in \overline{\mathbb{Z}_p}$.\\
	
	Let $\alpha, \beta \in K$.
	Then $\alpha^{p^n} = \alpha$ and $\beta^{p^n} = \beta$.
	Since $\overline{\mathbb{Z}_p}$ is a field of characteristic $p$, we have ${\color{blue}(\alpha+\beta)^{p^n} = \alpha^{p^n}+ \beta^{p^n}} = \alpha + \beta$.
	Thus, $(\alpha+\beta)$ is a zero of $x^{p^n}-x$.
	ie, $(\alpha + \beta) \in K$.
	Clearly, $(\alpha\beta)^{p^n} = \alpha^{p^n} \beta^{p^n} = \alpha\beta$.
	Thus, $\alpha\beta \in K$.\\


	Again $(-\alpha)^{p^n} = (-1 \cdot \alpha)^{p^n} = (-1)^{p^n} \cdot \alpha^{p^n} = -1 \cdot \alpha = -\alpha$.
	Thus, $-\alpha \in K$.
	Also $(\alpha^{-1})^{p^n} = \left( \frac{1}{\alpha} \right)^{p^n} = \frac{1}{\alpha^{p^n}} = \frac{1}{\alpha} = \alpha^{-1}$.
	Thus, $\alpha^{-1} \in K$.\\
	

	Trivially, $0,1 \in K$.
	Therefore, $K$ is a subfield of $\overline{\mathbb{Z}_p}$ with $p^n$ elements since {\color{blue}the $p^n$ zeroes of $x^{p^n}-x$ are distinct}.
\end{proof}

\begin{corollary}
	If $F$ is a finite field, then for every positive integer $n$, there exists an irreducible polynomial in $F[x]$ of degree $n$.
\end{corollary}
\begin{proof}
	Let $F$ be a finite field.
	Then $\mathbb{Z}_p$ is prime field of $F$ for some prime $p$.
	And $F$ is of characteristic $p$ and has $p^r$ elements for some positive integer $r$.\\ %The number of elements of $F$ should be multiple of prime $p$ and shouldn't be a multiple of any other prime $q$.


	Let $K$ be the subfield of $\overline{F}$ containing precisely all the zeroes of the polynomial $x^{p^{rn}}-x \in \mathbb{Z}_p[x]$.
	Then, $K$ has a subfield isomorphic to $\mathbb{Z}_p$ since $F$ is of characteristic $p$ and every subfield of $F$ has a subfield isomorphic to $\mathbb{Z}_p$.\\

	By existence theorem of Galois Fields, every element of $F$ is a zero of the polynomial $x^{p^r}-x \in \mathbb{Z}_p[x]$.
	That is, $\alpha \in F \iff \alpha^{p^r} = \alpha$.
	\begin{align*}
		\alpha^{p^{rn}} & = \left[\alpha^{p^r}\right]^{p^{r(n-1)}} & =  \alpha^{p^{r(n-1)}} & \\
		& = \left[\alpha^{p^r}\right]^{p^{r(n-2)}} & =  \alpha^{p^{r(n-2)}} & \\
		& \vdots & \vdots & \\
		& = \left[\alpha^{p^r}\right]^{p^r} & = \alpha^{p^r} & = \quad \alpha
	\end{align*}
	Thus, $\alpha \in F \implies \alpha^{p^{rn}} = \alpha \implies \alpha \in K$.
	Therefore $F$ is a subfield of $K$.
	Clearly, $K$ is a finite extension of the finite field $F$.
	And the vector space $K$ over $F$ is $n$-dimensional, since $K$ has $p^{rn} = [p^r]^n$ elements and $F$ has $p^r$ elements.\\
	
	Since every finite extension of finite fields are simple extensions, we have $K = F(\beta)$ and $irr(\beta,F) = n$.
	That is, there exists an unique monic, irreducible polynomial $p(x) \in F[x]$ of degree $n$ such that $p(\beta) = 0$.
	Therefore, $\forall n \in \mathbb{Z}^+$, there exists an irreducible polynomial in $F[x]$ of degree $n$.
\end{proof}


\begin{theorem}[Uniqueness of Galois Field]
	Let $p$ be a prime and $n$ a positive integer.
	If $E$ and $E'$ are fields of order $p^n$, then $E$ and $E'$ are isomorphic.\\

	There exists a unique finite field of order $p^n$, say \textbf{Galois Field}, $GF(p^n)$.
\end{theorem}
\begin{proof}
	Let $E,E'$ be fields of order $p^n$.
	Then both fields have $\mathbb{Z}_p$ as prime field.
	Thus, $E$ is a simple extension of $\mathbb{Z}_p$ of degree $n$.
	ie, $[E:\mathbb{Z}_p] = n$.
	And there exits an irreducible polynomial $f(x)$ such that $E \simeq \mathbb{Z}_p[x]/\generator{f(x)}$. \\


	Elements of $E$ are zeroes of $x^{p^n}-x$, thus $f(x)$ is a factor of $x^{p^n}-x$.
	Clearly, elements of $E'$ are zeroes of $x^{p^n}$ and therefore $E'$ has all zeroes of $f(x)$.
	And $E' \simeq \mathbb{Z}_p/\generator{f(x)}\simeq E$.
	Therefore, there exists a unique field of order $p^n$ (upto isomorphism), say $GF(p^n)$.
\end{proof}

\subsection{Exercise \S33}
\begin{enumerate}
	\item
\end{enumerate}

%Module 2
\pagebreak
{\Large Module  2 : Unique Factorisation Domains}
\section{Unique Factorisation Domains \S45}
\begin{definition}[divides]
	An element $a \in R$ divides $b$ if there exists an element $c \in R$ such that $b = ac$.
\end{definition}
\begin{definition}[associate]
	Two elements $a,b$ are associates if $a = bu$ where $u$ is a unit.
\end{definition}
\begin{definition}[UFD]
	\textbf{Unique factorisation domain}, UFD is an integral domain such that
	\begin{enumerate}
		\item Every element can be factored into a finite number of irreducibles, except 0 and units
		\dag\footnote{
			Unit is a element which has multiplicative inverse.}.
		\item The above factorisation is unique except for order and associates.
	\end{enumerate}
\end{definition}
\hrule\vspace{1em}
For example, In $\mathbb{Z}$, $24 = 2 \times 2 \times 2 \times 3 = -2 \times -3 \times 2 \times 2$.
Here $2$ and $-2$ are associates.
And $2$ and $3$ are not units, since $2^{-1}, 3^{-1} \notin \mathbb{Z}$.
\hrule\vspace{1em}
\begin{definition}[PID]
	An integral domain is $D$ is a \textbf{Principal Ideal Domain} if every ideal in $D$ is a principal ideal.
\end{definition}
%\subsection{Construction of UFD}
There are two important results on UFDs.
\begin{enumerate}
	\item Every PID is a UFD.
	\item If $D$ is a UFD, then $D[x]$ is a UFD.
\end{enumerate}

\subsection{Every PID is UFD}
%45.9
\begin{lemma}
	Let $R$ be a commutative ring and let $N_1 \subset N_2 \subset \dots $ be an ascending chain of ideals in $R$.
	Then $N = \cup_i N_i$ is an ideal of $R$.
\end{lemma}
\begin{proof}
	\textbf{Step 1 : $N$ is a subring of $R$}\\
	Suppose $N_i,\ N_j$ are two ideals in the chain, $N_i \subset N_j$ and $a \in N_i$, $b \in N_j$.
	Clearly, $a \in N_j$.\\

	And $a \pm b,\ ab \in N_j$.
	And $0 \in N_j \implies 0 \in N$.
	We have, $0$ in every ideal\dag\footnote{
		Suppose $b \in N$.
		We have $-b \in R$ and $-b+b = 0 \in bN \subset N$.}.
	Take $a = 0$, we know that for every element $b \in N_j$, its additive inverse $-b \in N_j$.
	Thus $b \in N \implies b \in N_j \implies -b \in N_j \implies -b \in N$.
	Clearly, $N$ is a subring of $R$.\\
	
	\textbf{Step 2 : $N$ is a ideal of $R$}\\
	Let $a \in N$ and $r \in R$.
	We have, $a \in N \implies a \in N_J$ for some ideal $N_j$ in the chain.
	Since $N_j$ is an ideal $ar = ra \in N_j$.
	Therefore, $ar \in N$.
	And $N$ is a ideal of $R$.
\end{proof}

\begin{lemma}[\textbf{A}scending \textbf{C}hain \textbf{C}ondition]
	Let $D$ be a PID.
	If $N_1 \subset N_2 \subset \dots$ is an ascending chain of ideal, then there exists a positive integer $r$ such that $N_r = N_s$ for every $s \ge r$.\\

	In other words, every strictly\dag\footnote{
		Strictly ascending chain : $N_1 \subsetneq N_2 \subsetneq N_3 \subsetneq \dots \subsetneq N_k$.}
	ascending chain of ideals in a PID is of finite length.
\end{lemma}
\begin{proof}
	Let $D$ be an integral domain.
	And $N_1 \subseteq N_2 \subseteq \dots$ be an ascending chain of ideals in $D$.
	Then $N = \cup_i N_i$ is an ideal in $D$.
	Since $D$ is a PID, by definition of \textbf{p}rincipal \textbf{i}deal \textbf{d}omain every ideal in it is a principal ideal.
	Thus, $N$ is a principal ideal in $D$.
	That is, there exists $c \in D$ such that $\generator{c} = N$.\\

	Since $c \in N$, and $N = \cup_i N_i$ we have $c \in N_r$ for some $r \in \mathbb{N}$.
	Then $\generator{c} = N_r = N$.
	Again, $N_r \subset N_s \implies c \in N_s \implies \generator{c} = N_s = N$.\\

	Suppose the chain of ideals are strictly ascending, that is every ideal in the chain is properly containing the former ideal.
	Then, the ideal $N_r$ such that $c \in N_r$ is the last ideal in its chain.
	Thus, striclty ascending chain of ideals is finite.
\end{proof}

\begin{theorem}
	Let $D$ be a PID.
	Every element that is neither $0$ nor a unit in $D$ is a product of irreducibles.
\end{theorem}
\begin{proof}
	Suppose $D$ is a PID.
	And suppose $a \in D$ is a neither a zero nor a unit.
	If $a$ is an irreducible, then the result is trivial.
	Suppose $a$ is not an irreducible.\\

	\textbf{Step 1 : $a$ has an irreducible factor}\\
	By the definition of irreducibility, $a$ has a factorisation $a = a_1b_1$ where $a_1,b_1$ are non-units.
	And every element $ar \in \generator{a}$ can be expressed as $ar = a_1b_1r = a_1r' \in \generator{a_1}$.
	Thus, the ideal generated by $a$, $\generator{a}$ is contained in the ideal generated by $a_1$, $\generator{a_1}$.
	That is, $\generator{a} \subset \generator{a_1}$.\\

	If $a_1$ is an irreducible, then the proof is complete.
	Suppose $a_1$ is not an irreducible.
	That is, $a_1 = a_2b_2$.
	Then $\generator{a_1} \subset \generator{a_2}$.
	Also we have, $\generator{a_1} \ne \generator{a_2}$.\\

	Suppose $\forall d \in D,\ a_2d \in \generator{a_1} \implies a_2\cdot 1 = a_2 \in \generator{a_1} \implies a_2 = a_1c_2 \implies a_1 = (a_1c_2)b_2 \implies c_2b_2 = 1 \implies b_2$ has multiplicative inverse $c_2$. This contradicts the assumption that $b_2$ is a unit.\\

	Continuing like this, we get a {\color{red}strictly} ascending chain of ideals $\generator{a} \subsetneq \generator{a_1} \subsetneq \generator{a_2}, \dots $.
	And we know that, every strictly ascending chain of ideals is finite.
	Thus, $a_r$ is an irreducible.
	And $a = a_1b_1 = (a_2b_2)b_1 = \dots = a_r(b_rb_{r-1}\dots b_1) = a_rb$.
	Clearly, $a$ has an irreducible factor $a_r$.\\

	\textbf{Step 2 : $a$ is a product of irreducibles}\\
	Suppose $a$ is neither zero nor a unit.
	Then $a = p_1c_1$ where $p_1$ is an irreducible and $c_1$ is not a unit.
	Continuing like this, we get another striclty ascending chain of ideals $\generator{a} \subsetneq \generator{c_1} \subsetneq \generator{c_2} \subsetneq \dots$ such that $a = p_1c_1 = p_1(p_2c_2) = \dots$ where $p_1,p_2,\dots$ are irreducibles and $c_j$ are non-units.
	Again, by ascending chain condition this strictly ascending chain is finite.
	That is, $a = p_1p_2\dots p_kc_k$ for some $k \in \mathbb{N}$.
	Since $\generator{c_k}$ is a maximal ideal in $D$, $c_k$ is an irreducible say, $p_{k+1}$.
	Thus, any element $a \in D$ (except zero and units) can be expressed as product of irreducibles.
\end{proof}

\subsection{Irreducible element and Maximal Ideal}
We have seen earlier that a non-trivial principal ideal $\generator{p(x)}$ in $F[x]$ is maximal if and only if the generator $p(x)$ is irreducible over $F$.
Now we have a generalisation, which says ideals in PIDs are maximal if and only if the generator is irreducible.
Remember that for any field $F$, $F[x]$ is a PID.
\begin{lemma}
	An ideal $\generator{p}$ in a PID is maximal if and only if $p$ is an irreducible.
\end{lemma}
\begin{proof}
	\textbf{Part A : $\generator{p}$ maximal in $D \implies p$ irreducible in $D$}\\
	Let $D$ be a PID.
	Suppose $\generator{p}$ is a maximal ideal in $D$.
	Suppose $p = ab$ in $D$.
	That is, $p = ab$ where $a,b \in D$.
	Then, $\generator{p} \subset \generator{a}$.\\

	Suppose $\generator{p} = \generator{a}$.
	Then $a = pc = (ab)c \implies bc = 1$ and $b$ is a unit.\\

	Suppose $\generator{p} \ne \generator{a}$.
	Then $\generator{a} = D$, since $\generator{p}$ is a maximal ideal.
	That is $\generator{a} = \generator{1} \implies a,1$ are associates.
	And $a$ is a unit.\\

	Thus for any factorisation $p = ab$, either $a$ or $b$ is a unit.
	Therefore, $p$ is an irreducible.\\

	\textbf{Part B : $p$ is irreducible in $D \implies \generator{p}$ is maximal in $D$}\\
	Suppose $p$ is an irreducible in $D$.
	Then $p = ab$ where $a,b \in D $ implies that either $a$ or $b$ is a unit.
	Since $p = ab$, $\generator{p} \subset \generator{a}$.
	We know that, if $a$ is a unit then $\generator{a} = \generator{1} = D$.\\

	Suppose $a$ is not a unit.
	Then $b$ is a unit.
	That is, there exists $u \in D$ such that $bu = 1$.
	Then $pu = abu= a$.
	Thus, $\generator{a} \subset \generator{p} \implies \generator{p} = \generator{a}$.\\

	Thus, for any factorisation $p = ab$, the ideals generated by $a,b$ are either $D$ or $\generator{p}$ itself.
	In other words, there doesn't exist a proper ideal containing $\generator{p}$.
	Therefore, $\generator{p}$ is a maximal ideal in $D$.
\end{proof}

\subsection{Every PID is UFD}
	We have seen earlier that $F[x]$ has unique factorisation of all its elements.
	Now, we generalise that result into ``every PID has unique factorisation for all its elements''.

\begin{lemma}
	In a PID, if an irreducible $p$ divides $ab$, then either $p|a$ or $p|b$.
\end{lemma}
\begin{proof}
	Let $D$ be a PID.
	Suppose $p \in D$ is irreducible.
	Suppose $p | ab$.
	Then $ab \in \generator{p}$.
	And we have, $\generator{p}$ is a maximal ideal.
	However, every maximal ideal in $D$ is a prime ideal.
	Thus, $ab \in \generator{p} \implies a \in \generator{p} \text{ or } b \in \generator{p}$.
	In other words, $p | a$ or $p | b$.
\end{proof}

\begin{corollary}
	If $p$ is an irreducible in a PID $D$ and $p$ divides $a_1a_2\dots a_n$ where $a_i \in D$, then $p|a_i$ for at least one $i$.
\end{corollary}
\begin{proof}
	We know that, $p | a_1a_2 \implies p | a_1 \text{ or } p | a_2$.\\
	Suppose $p | a_1a_2\dots a_k \implies p| a_1 \text{ or } p | a_2 \dots \text{ or } p | a_k$.\\
	Suppose $p | a_1a_2\dots a_{k+1} \implies p | a_1a_2\dots a_k \text{ or } p | a_{k+1}$.\\
	$\implies p|a_1 \text{ or } p|a_2 \text{ or } \dots p|a_k \text{ or } p | a_{k+1}$.\\
	That is, if $p$ divides a finite product, then it divides at least one of them.
\end{proof}

\begin{definition}
	A nonzero, nonunit element $p$ in an integral domain $D$ is a prime if $\forall a,b \in D,\ p|ab \implies p|a \text{ or } p|b$.
\end{definition}

\begin{theorem}
	Every PID is a UFD.
\end{theorem}
\begin{proof}
	Let $D$ be a PID.
	Let $a \in D$ is neither a zero nor a unit.
	Then $a$ has a factorisation into irreducibles $a= p_1p_2\dots p_r$. 
	Suppose $a$ has another factorisation $a = q_1q_2\dots q_s$.\\

	We have $p_1 | q_1q_2\dots q_s$.
	Thus, $p_1$ divides at least one of them, say $q_j$.
	Without loss of generality, we assume that $p_1 | q_1$ (rearranging the terms if necessary).\\

	Since $q_1$ is an irreducible, $q_1 = p_1u_1 \implies u_1$ is a unit.
	Thus, $p_1p_2 \dots p_r = p_1u_1q_2q_3\dots q_s$.
	That is, $p_2p_3 \dots p_r = u_1 q_2q_3\dots q_s$.\\

	Continuing like this we get, $p_r = u_1u_2\dots u_{r-1} p_ru_rq_{r+1}q_{r+s}\dots q_s$.
	Thus $u_1u_2\dots u_rq_{r+1}q_{r+2}\dots q_s$ is a unit.
	We have $s = r$, otherwise $1 = u_1u_2\dots q_{r+1}\dots$ is a contradiction.
	Therefore, any element $a \in D$ has a unique factorisation except for order,associates and units.
\end{proof}

\begin{corollary}
	The integral domain $\mathbb{Z}$ is a UFD.
\end{corollary}
\begin{proof}
	The ideals in $\mathbb{Z}$ are of the form $n\mathbb{Z}$ where $n \in \mathbb{Z}$.
	Thus every ideal in $\mathbb{Z}$ are pricipal ideals.
	Therefore, $\mathbb{Z}$ is a PID.
	We know that every PID is a UFD.
	Thus, $\mathbb{Z}$ is a \textbf{u}nique \textbf{f}actorisation \textbf{d}omain.
\end{proof}

\subsection{$D$ is UFD $\implies D[x]$ is UFD}
\begin{definition}[gcd]
	Let $D$ be a UFD and $a_1,a_2,\dots,a_n$ be nonzero elements in $D$.
	An element $d \in D$ is a \textbf{g}reatest \textbf{c}ommon \textbf{d}ivisor of $a_i$ if $d$ is a common divisor of all $a_i$s and also divides any common divisor of $a_i$s.
\end{definition}

\begin{definition}[primitive]
	Let $D$ be a UFD.
	A nonconstant polynomial $a_0 + a_1x + \dots + a_nx^n \in D[x]$ is a primitive if $1$ is the gcd of all $a_i$s.
\end{definition}
	For exmaple, $4x^3+3x^2+2 \in \mathbb{Z}[x]$ is a primitive since $\gcd(4,3,2) = 1$.

\begin{lemma}
	If $D$ is a UFD, then for every nonconstant $f(x) \in D[x]$ we have $f(x) = cg(x)$ where $c \in D$ and $g(x) \in D[x]$ and $g(x)$ is primitive.
	The element $c \in D$ is unique upto a unit factor in $D$ and is the \textbf{content} of $f(x)$.
	Also $g(x)$ is unique upto a unit factor in $D$.
\end{lemma}
\begin{proof}
	\textbf{Step 1 : There exists $c \in D$ such that $f(x) = cg(x)$}\\
	Let $f(x) = a_0 + a_1x + \dots +a_nx^n$ be a non-constant polynomial in $D[x]$.
	Let $c = gcd(a_0,a_1,\dots,a_n)$.
	In other words, $c$ is the greatest common divisor of the coefficients of $f(x)$.
	Let $q_i = ca_i)$.
	Clearly, $gcd(q_1,q_2,\dots,q_n) = 1$.
	Thus, we have $f(x) = cg(x)$ where $g(x) = q_0+q_1x+\dots+q_nx^n)$ is a primitive.\\

	\textbf{Step 2 : There exists unique $c$ such that  $f(x) = cg(x)$}\\
	Suppose $f(x) = cg(x) = dh(x)$ where $c,d \in D$ and $g(x), h(x)$ are primitives.\\

	Clearly, $c$ and $d$ are associates.
	Otherwise, there exists an irreducible element $p$ such that $p | cg(x)$ but $p\!\not|\ dh(x)$ which is a contradiction.
	Thus, we can cancel all irreducible factors of $c$ to obtain, $ug(x) = vh(x)$ where $u$ and $v$ are units.
	Therefore, the content of $f(x)$, $c$ unique upto associates.\\

	Again, $f(x) = cg(x) = (cu) (u^{-1}g(x))$ and thus $g(x)$ is unique upto associates/units.
\end{proof}

\begin{definition}[content]
	Let $D$ be a UFD.
	Let $f(x) \in D[x]$.
	Then $f(x) = cg(x)$ for some primitive $g(x) \in D[x]$ and $c \in D$.
	The element $c$ which is unique upto units, is the content of $f(x)$.
\end{definition}
\hrule\vspace{1em}
	For example, Let $f(x) = 8x^3+6x^2+4 \in \mathbb{Z}[x]$.
	Then $f(x) = 2(4x^3+3x^2+2)$ where $4x^3+3x^2+2 \in \mathbb{Z}[x]$ is a primitive and $2 \in \mathbb{Z}$.
	Thus, $content(f) = 2$.
\hrule\vspace{1em}
\begin{lemma}[Gauss]
	If $D$ is a UFD, then product of two primitive polynomials in $D[x]$ is again primitive.
\end{lemma}
\begin{proof}
	Let $f(x) = a_0 + a_1x + \dots + a_nx^n$ and $g(x) = b_0 + b_1x + \dots + b_mx^m$.
	Suppose $f(x)$ and $g(x)$ are primitives.
	Let $h(x) = f(x)g(x) = c_0 + c_1x + \dots + c_{n+m}x^{n+m}$.
	Let $p$ be an irreducible in $D$.
	Then $f(x)$ has a coefficient which is not divisible by $p$.
	Suppose $p$ divides every coefficient $f(x)$, then $f(x)$ is not a primitive.\\

	Let $r$ be the smallest integer such that $p\not\!|\ a_r$.
	Similarly, let $s$ be the smallest integer such that $p\not|\ b_s$.
	Now consider the coefficient $c_{r+s}$ of $h(x)$.
	\[ c_{r+s} = a_0b_{r+s}+\dots+a_{r-1}b_{s+1}+a_rb_s+a_{r+1}b_{s-1}+\dots+a_{r+s}b_0 \]
	By the selection of $r$, $p | a_j$ for every $j < r$.
	Thus, $p | a_0b_s+\dots+a_{r-1}b_{s+1}$.
	Similarly, by the selection of $s$, $p | b_k$ for every $k < s$.
	Thus, $p | a_{r+1}b_{s-1}+\dots+a_0b_s$.
	Clearly, $p | c_{r+s} \iff p | a_rb_s \implies p|a_r \text{ or } p|b_s$.
	This is not possible, thus $p \not| c_{r+s}$.	
	Thus, for any irreducible $p \in D$, $h(x)$ has a coefficient which is not divisible by $p$.
	Therefore, product of two primitives is always a primitive.
\end{proof}

\begin{corollary}
	If $D$ is a UFD, then a finite product of primitive polynomials in $D[x]$ is again primitive.
\end{corollary}
\begin{proof}
	Let $\{f_k\}_{k=1}^n$ be a family of primitives.
	Then $f_1(x)f_2(x)$ is a primitive, since product of two primitives is always a primitive.\\

	Suppose $g(x) = f_1(x)f_2(x)\dots f_k(x)$ is a primitive.\\

	Consider $h(x) = f_1(x)f_2(x)\dots f_{k+1}(x) = g(x)f_{k+1}(x)$.
	Since both $g(x)$ and $f_{k+1}(x)$ are primitives their product $h(x)$ is also a primitive.\\

	Thus by finite mathematical induction, every finite product of primitives is a primitive.
\end{proof}

\begin{lemma}
	Let $D$ be a UFD and let $F$ be a field of quotients of $D$.
	Let $f(x) \in D[x]$ where $\deg f(x) > 0$.
	If $f(x)$ is an irreducible in $D[x]$, then $f(x)$ is also an irreducible in $F[x]$.
	Also, if $f(x)$ is primitive in $D[x]$ and irreducible in $F[x]$, then $f(x)$ is irreducible in $D[x]$.
\end{lemma}
\begin{proof}
	Let $D$ be a UFD and $F$ be the field of quotients of $D$.
	Then elements of $F$ are of the form $(a,b) \in D \times D$.
	Also $(a,b)+(c,d)  = (ad+bc,bd)$ and $(a,b)\cdot (c,d) = (ac,bd)$.
	And we say express $(a,b)$ as $a/b$.\\

	\textbf{Part 1 : irreducible in $D[x] \implies$ irreducible in $F[x]$}\\
	Let $f(x) \in D[x]$ be an irreducible in $D[x]$.
	Suppose $f(x)$ is not irreducible in $F[x]$.
	Then $f(x) = r(x)s(x)$ where $r(x),s(x) \in F[x]$.\\

	The coefficients of $r(x)$ are of the form $a/b$.
	By multiplying $r(x)$ with the product of all denominators, we can remove its denominators and obtain an associate $r_1(x) \in D[x]$.
	Similarly, we have $s(x) = vs_1(x)$ where $s_1(x) \in D[x]$.
	Thus, $f(x) = r(x)s(x) = ur_1(x)vs_1(x) = uv r_1(x)s_1(x)$.
	Therefore, $f(x) \in D[x]$ is not an irreducible, which is a contradiction.
	Thus, $f(x)$ is irreducible in the quotient field $F$ as well.\\

	\textbf{Part 2 : irreducible in $F[x] \implies$ irreducible in $D[x]$}\\
	Suppose $f(x) \in D[x]$ is irreducible in $F[x]$.	
	Clearly, $F$ contains a UFD isomorphic to $D$.
	Thus $D[x] \le F[x]$.
	Therefore, any polynomial irreducible in $F[x]$ is also irreducible in $D[x]$.
\end{proof}
	We just saw that if $F$ is the quotient field of a UFD $D$ and $f(x) \in D[x]$. The irreducibility of $f(x)$ in $F[x]$ is necessary and sufficient for the irreducibility of $f(x)$ in $D[x]$. Now we prove that the factorisation is also unique upto a morphism.

\begin{corollary}
	If $D$ is a UFD and $F$ is a field of quotients of $D$, then a nonconstant polynomial $f(x) \in D[x]$ factors into a product of two polynomials of lower degrees $r$ and $s$ in $F[x]$ if and only if it has a factorization into polynomials of the same degress $r$ and $s$.
\end{corollary}
\begin{proof}
	We know that if $f(x) \in D[x]$ has a factorisation $f(x) = r(x)s(x)$ in $F[x]$.
	Then it has a factorisation in $D[x]$ as well, $f(x) = cr_1(x)s_1(x)$ where $r_1(x),s_1(x)$ are associates of $r(x), s(x)$ in $F[x]$.
	Clearly, the associates are always of the same degree.\\

	Trivially, any factorisation in $D[x]$ will also be a factorisation in $F[x]$.
	And the factors will have the same degree, unless $D[x]$ has an irreducible polymonial which is not irreducible in $F[x]$.
	This is not possible.
\end{proof}

\begin{theorem}
	If $D$ is a UFD, then $D[x]$ is a UFD.
\end{theorem}
\begin{proof}
	Let $f(x) \in D[x]$.
	Suppose $deg(f) > 0$.
	Otherwise, $f(x)$ is a constant and we have trival factorisation.\\
	
	Let $f(x) = g_1(x)g_2(x)\dots g_r(x)$ be a factorisation in $D[x]$ with maximum number of factors.	
	Then $f(x) = c_1h_1(x)c_2h_2(x)\dots c_rh_r(x)$ where $g_k(x) = c_kh_k(x)$ and $h_k(x)$ are primitives.
	And $h_k(x)$ are irreducibles.
	Otherwise, $f(x)$ has a factorisation with greater number of factors than $r$ which is a contradiction.
	Thus, $f(x) = uh_1(x)h_2(x)\dots h_r(x)$ is a factorisation of $f(x)$ into a product of irreducibles.\\

	Suppose $f(x)$ has another factorisation $f(x) = G_1(x)G_2(x)\dots G_r(x)$.
	Then $f(x) = vH_1(x)H_2(x)\dots H_r(x)$ with $H_k(x)$ are all irreducibles.
	We know that, $h_k(x) | f(x) \implies h_k(x) | H_1(x)H_2(x)\dots H_r(x) \implies h_k(x) | H_k(x)$ (WLOG).
	Therefore, the factorisation is unique.
\end{proof}
\hrule\vspace{1em}
For example, let $x,y$ be two indeterminates, then an element $f(x) \in F[x,y]$ is of the form $\displaystyle\sum_{i,j = 0}^{n,m} a_{ij}x^i y^j$.
\hrule\vspace{1em}
\begin{corollary}
	If $F$ is a field of quotients and $x_1,x_2,\dots,x_n$ are indeterminates, then $F[x_1,x_2,\dots,x_n]$ is a UFD.
\end{corollary}
\begin{proof}
	Suppose $D$ is a UFD and $F$ is its field of quotients, then $F[x]$ is a UFD.\\

	Suppose $K = F[x_1,x_2,\dots,x_k]$ is a UFD.\\

	Then, $F[x_1,x_2,\dots,x_k,x_{k+1}] = F[x_1,x_2,\dots,x_k][x_{k+1}] = K[x_{k+1}] = K[x]$ is a UFD.
\end{proof}

\subsection{Exercise \S45}
\begin{enumerate}
	\item
\end{enumerate}

\section{Euclidean Domain \S46}
\begin{definition}[Euclidean Norm]
	Euclidean norm on an integral domain $D$ is a function $v$ which maps non-zero elements of $D$ into non-negative integers such that 
	\begin{enumerate}
		\item $\forall a,b \in D, (b \ne 0)$ there exists $q,r \in D$ such that $a = qb + r$ where  either $r = 0$ or $v(r) < v(b)$ and 
		\item $\forall a,b \in D, (a,b \ne 0)$ $v(a) \le v(ab)$
	\end{enumerate}
\end{definition}
\begin{definition}[Euclidean Domain]
	An integral domain $D$ is a Euclidean Domain if there exists a Euclidean Norm in $D$.
\end{definition}
\hrule\vspace{1em}
For example, $v(n) = |n|$ is a Euclidean norm on Euclidean domain $\mathbb{Z}$. And $v(f(x)) = deg(f(x))$ is a Euclidean norm on Euclidean domain $F[x]$.
\hrule\vspace{1em}
\begin{theorem}
	Every Euclidean domain is a PID.
\end{theorem}
\begin{proof}
	Let $D$ be a Euclidean domain with Euclidean norm $v$.
	Let $N$ be an ideal in $D$.
	If $N = \{ 0\}$, then $N = \generator{0}$ is a principal ideal.\\

	Suppose $N \ne \{ 0 \}$.
	Then there exists $b \in N\ (b \ne 0)$.
	Clearly, $b \in N \implies \generator{b}\subset N$.
	Choose a $b \in N$ such that $v(b)$ is minimal in $N$.\\

	\textbf{Claim : $N = \generator{b}$}\\
	Let $a \in N$.
	Then there exists $q,r \in D$ such that $a = qb + r$ where $r = 0$ or $v(r) < v(b)$.
	Clearly, $r = a-qb \in N$.
	Thus, $r = 0$ since $v(r) < v(b)$ and $v(b)$ is minimal in $N$.
	That is, $a = qb$ or $b|a$ for every $a \in N$.
	Thus, $N \subset \generator{b}$.
	Therefore, $N = \generator{b}$.
	In other words, evey ideal in $D$ is a principal ideal.
\end{proof}

\begin{corollary}
	Every Euclidean domain is a UFD.
\end{corollary}
\begin{proof}
	We know that, every Euclidean domain is a PID.
	And every PID is a UFD.
	Thus, every Euclidean domain is a UFD.
\end{proof}
\subsection{Arithmetic in Euclidean Domain}
\begin{theorem}
	For a Euclidean domain with Euclidean norm $v$, $v(1)$ is minimal and $u \in D$ is a unit if and only if $v(u) = v(1)$.
\end{theorem}
\begin{proof}
	We have, $v(a) \le v(ab)$.
	Take $a = 1$, $v(1) \le v(1b) \implies v(1) \le v(b)$ for every $b \in D$.
	Thus, $v(1)$ is minimal.\\

	Suppose $u$ is a unit with multplicative inverse $u^{-1}$.
	Clearly, $v(1) \le v(u)$ since $u \in D$.
	Take $a = u$ and $b = u^{-1}$.
	Then $v(u) \le v(uu^{-1}) = v(1)$.
	Therefore, for every unit $u \in D$, we have $v(u) = v(1)$.
\end{proof}

\begin{theorem}[division algorithm]
	Let $D$ be a Euclidean domain with Euclidean norm $v$.
	And $a,b \in D\ (a,b \ne 0)$.
	\begin{align*}
		a = & bq_1 + r_1, \text{ where } r_1 = 0 \text{ or } v(r_1) < v(b)
		\intertext{if $r_1 \ne 0$}
		b = & r_1q + r_2, \text{ where } r_2 = 0 \text{ or } v(r_2) < v(r_1)
		\intertext{ In general, if $r_i \ne 0$}
		r_{i-1} = & r_iq + r_{i+1} \text{ where } r_{i+1} = 0 \text{ or } v(r_{i+1}) < v(r_i)
	\end{align*}
	Then the sequence $r_1,r_2, \dots$ must terminate with some $r_s = 0$.\\

	If $r_1 = 0$, then $gcd(a,b) = b$.\\
	If $r_k = 0$, then $gcd(a,b) = r_{k-1}$.\\

	Furthermore, if $d$ is a gcd of $a$ and $b$, then there exists $\lambda,\mu \in D$ such that $d= \lambda a + \mu b$.
\end{theorem}
\begin{proof}
	\textbf{Step 1 : Finite Sequence  $r_1,r_2,\dots,r_s$}\\
	Suppose $r_1,r_2,\dots,r_{i-1} \ne 0$.
	Then $v(r_1) > v(r_2) > \dots > v(r_{i-1})$ is a strictly decreasing sequence of non-negative integers.
	Thus, the sequence will terminate in finite numbers of steps.
	That is, $r_s = 0 $ for some integer $s$.\\
	
	\textbf{Step 2 : $gcd(a,b) = r_{s-1}$}\\
	Suppose $r_1 = 0$.
	Then $a = bq$ and $gcd(a,b) = b$ since $b|a, b|b$ and there does not exist an integer greater than $b$ that divides $b$.\\

	Suppose $r_1 \ne 0$ and $gcd(a,b) = d$.
	Then $r_1 = a-bq$ and $d|r_1$.\\
	And $d | b, d | r_1 \implies d|a$ since $a = qb+r_1$.
	Thus, $gcd(a,b) = gcd(b,r_1)$.\\
	Continuing like this, we get $gcd(a,b) = gcd(r_{s-2},r_{s-1})$ if $r_{s-1} \ne 0$.\\
	And we have, $r_s = 0 \implies r_{s-2} = qr_{s-1}$.\\
	Clearly, $gcd(r_{s-2},r_{s-1}) = r_{s-1} = gcd(a,b)$.\\

	\textbf{Step 3 : $gcd(a,b) = \lambda a + \mu b$}\\
	Let $b$ be a $gcd(a,b)$.
	Then, $b = 0a+1b$ and result is complete.\\

	Suppose $gcd(a,b) = r_{s-1}$.
	And $r_{s-1} = r_{s-3} - qr_{s-2}$.
	Clearly, $r_i = \lambda_i r_{i-2} + \mu_i r_{i-1}$.
	Keep on substituting using these equations until we reach $r_{s-1} = \lambda a + \mu b$.\\

	Suppose $d'$ is another $gcd(a,b)$.
	Then $d' = ud$ is an associate of $d$.
	And $d' = ud = (\lambda u)a + (\mu u) b$.
	And the result is true for any $gcd(a,b)$.
\end{proof}

\section{Gaussian Integers and Multiplicative Norms \S47}
\subsection{Gaussian Integers and Norm}
\begin{definition}[Gaussian integers]
	Gaussian integers are complex numbers of the form $a+ib$ where $a,b \in \mathbb{Z}$.
\end{definition}
Note : Let $\alpha = a+ib$.
Clearly, Gaussian integers are elements of $\mathbb{Z}[i]$.
Here, $\mathbb{Z}[i]$ is a simple extension of the integral domain $\mathbb{Z}$ with a zero of $x^2+1$.

\begin{definition}[Gaussian Norm]
	Let $\alpha = a+ib$ be a Gaussian integer.
	Then $N(\alpha) = |\alpha|^2 = a^2+b^2$ is a Euclidean norm on $\mathbb{Z}[i]$.
\end{definition}

\begin{lemma}
	The Gaussian norm $N : \mathbb{Z}[i] \to \mathbb{Z}$ defined by $N(a+ib) = a^2+b^2$ has the following properties
	\begin{enumerate}
		\item $N(\alpha) \ge 0,\ \forall \alpha \in \mathbb{Z}[i]$
		\item $N(\alpha) = 0 \iff \alpha = 0$
		\item $N(\alpha\beta) = N(\alpha)N(\beta)$
	\end{enumerate}
\end{lemma}
\begin{proof}
	We have $\alpha \in \mathbb{Z}[i]$.
	Then $\alpha = a+ib$ where $a,b \in \mathbb{Z}$.
	Clearly, $N(a+ib) = a^2+b^2 \ge 0$.\\

	$N(\alpha) = 0 \iff a^2+b^2 = 0 \iff a=0,b=0 \iff \alpha = 0+i0 = 0$.\\

	Also, $N(\alpha\beta) = |\alpha\beta|^2 = |\alpha|^2 |\beta|^2 = N(\alpha)N(\beta)$.
\end{proof}

\begin{lemma}
	$\mathbb{Z}[i]$ is an integral domain.
\end{lemma}
\begin{proof}
	Let $\alpha, \beta \in \mathbb{Z}[i]$.\\
	Then, $\alpha + \beta = (a+ib) + (c+id) = (a+c) + i(b+d) = (c+a) + i(d+b) = \beta + \alpha$.
	And for any $\alpha \in \mathbb{Z}[i]$, we have $\alpha \cdot 1 = (a+ib) \cdot (1+i0) = (a+ib)$.
	Thus, we have $\mathbb{Z}[i]$ is a commutative ring with unity.\\

	It remains to prove that $\mathbb{Z}[i]$ has no zero divisors.
	Suppose $\alpha\beta = 0$.
	$\alpha\beta = 0 \implies N(\alpha\beta) = 0 \implies N(\alpha) N(\beta) = 0$.
	But, $N(\alpha),N(\beta) \in \mathbb{Z}$ and $\mathbb{Z}$ has no zero divisors.
	Thus, $N(\alpha) = 0$ or $N(\beta) = 0 \implies \alpha = 0$ or $\beta = 0$.
	Therefore $\mathbb{Z}[i]$ has no zero divisors.
\end{proof}

\begin{theorem}[Gaussian integers is a Euclidean Domain]
	The function $v$ defined by $v(\alpha) = N(\alpha)$ for every non-zero $\alpha \in \mathbb{Z}[i]$ is a Euclidean norm.
\end{theorem}
\begin{proof}
	\textbf{Step 1 : $v(a) \le v(ab)$}\\
	Let $\beta = b_1 + ib_2$ and $\beta \ne 0$.
	Then $N(\beta) = b_1^2+b_2^2 \ge 1$.
	Thus, $N(\alpha) \le N(\alpha)N(\beta) = N(\alpha\beta)$.\\

	\textbf{Step 2 : Division algorithm}\\
	That is, $\forall \alpha,\beta \in \mathbb{Z}[i],(\beta \ne 0)\ \exists \sigma,\rho \in \mathbb{Z}[i]$ such that $\alpha = \beta\sigma+\rho$, and $\rho = 0$ or $v(\rho) < v(\beta)$.

	Since $\beta \ne 0$, $\alpha/\beta$ exists.
	And we have, $\frac{\alpha}{\beta} = \frac{a_1+ia_2}{b_1+ib_2} = \frac{(a_1+ia_2)(b_1-ib_2)}{(b_1+ib_2)(b_1-ib_2)} = \frac{a_1b_1+a_2b_2}{b_1^2+b_2^2} + i \frac{a_2b_1-a_1b_2}{b_1^2+b_2^2} = r+is$ where $r,s \in \mathbb{Q}$.
	Consider integers $q_1,q_2$ that are nearest to the rational numbers $r,s$.
	Define $\sigma = q_1 + iq_2 \in \mathbb{Z}[i]$ and $\rho = \alpha - \beta\sigma$.\\

	Suppose $\rho \ne 0$.
	If $\rho = 0$, then the proof is complete.
	By definition of $\sigma$, $|q_1-r| \le 0.5$ and $|q_2-s| \le 0.5$.
	And we have,
	\[ N \left(\frac{\alpha}{\beta} - \sigma \right) = N((r-q_1)+i(s-q_2)) = |q_1-r|^2 + |q_2-s|^2 \le 0.5 \]
	Since $\alpha = \beta\sigma + \rho$,
	we have $\rho = \beta(\frac{\alpha}{\beta}-\sigma)$
	\[N(\rho) = N \left( \beta \left(\frac{\alpha}{\beta}-\sigma \right) \right) = N(\beta) N \left(\frac{\alpha}{\beta}-\sigma\right) \le 0.5N(\beta)\]
	Thus, $N(\rho) < N(\beta)$.
	Therefore, Gaussian integers is a Euclidean domain.
\end{proof}

\subsection{Multiplicative Norm}
\begin{definition}[multiplicative norm]
	Let $D$ be an integral domain. A function $N : D \to \mathbb{Z}$ is a multiplicative norm if 
	\begin{enumerate}
		\item $N(\alpha) = 0 \iff \alpha = 0$
		\item $N(\alpha\beta) = N(\alpha)N(\beta),\ \forall \alpha,\beta \in D$
	\end{enumerate}
\end{definition}
Note : Guassian norm is a multiplicative norm.

\begin{theorem}
	Let $D$ be an integral domain with multiplicative norm $N$.
	Then $N(1) = 1$ and $|N(u)| = 1$ for any unit $u$.
	Suppose $|N(\alpha)| = 1$ only for units  in $D$.
	Then $N(\alpha)$ is a prime in $\mathbb{Z}$ implies $\alpha$ is an irreducible in $D$.
\end{theorem}
\begin{proof}
	We know, $N$ is a multiplicative norm.
	Thus, $N(1) = N(1 \ast 1) = N(1)N(1) \implies N(1) = 1$.\\

	Suppose $u$ is a unit in $D$.
	Then $1 = N(1) = N(uu^{-1}) = N(u) N(u^{-1})$
	Since $1$ has only two factors $\pm 1 \in \mathbb{Z}$, we have $|N(u)| = 1$.\\

	Suppose $|N(\alpha)| = 1$ only if $\alpha$ is a unit in $D$.
	Suppose $\alpha \in D$ and $|N(\alpha)| = p$, where $p$ is a prime in $\mathbb{Z}$.
	Suppose $\alpha$ is not an irreductible.
	Then $\alpha$ has a factorisation $\alpha = \beta\gamma$ where $\beta,\gamma \in D$ are non-units.
	Then $p = N(\alpha) = N(\beta\gamma) = N(\beta)N(\gamma)$.
	We have, $\beta,\gamma$ are non-units and $|N(\beta)| \ne 1$ and $|N(\gamma)| \ne 1$.
	This is not possible.
	Therefore, $\alpha$ is an irreducible in $D$.
\end{proof}

\subsection{Applications of multiplicative norm}
\subsubsection{The integral domain $\mathbb{Z}[\sqrt{-5}]$ is not a UFD.(\S47.9)}
\begin{proof}
Elements of $\mathbb{Z}[\sqrt{-5}]$ are of the form $a+b\sqrt{-5}$ and $N(a+b\sqrt{-5}) = a^2 + 5b^2$.
If $N(a+b\sqrt{-5}) = a^2+5b^2 = 1$, then, $a = \pm 1$ and $b = 0$.
Clearly, $|N(\alpha)| = 1$ only if $\alpha$ is a unit in $\mathbb{Z}[\sqrt{-5}]$.\\

The element $3 \in \mathbb{Z}[\sqrt{-5}]$ is an irreducible.
Suppose $3$ is not an irreducible.
That is, there is a factorisation $3 = \beta\gamma$ where $\beta,\gamma$ are non-units.
Then $9 = N(3) = N(\beta)N(\gamma)$ where $\beta,\gamma$ are non-units.
The integer factors of $9$ are $1,3,9$.
Thus, $N(\beta) = N(\gamma) = 3$.
Otherwise $N(\beta) = 1$ or $N(\gamma) = 1$.
But, there doesn't exist an element $a+b\sqrt{-5}$ such that $N(a+b\sqrt{-5}) = 3$.
Similarly, $7 \in \mathbb{Z}[\sqrt{-5}]$ is an irreducible.
We have, $49 = N(7) = N(\beta)N(\gamma) \implies N(\beta)=N(\gamma) = 7$ is not possible since there are no elements of norm $7$ in $\mathbb{Z}[\sqrt{-5}]$.\\

Suppose $(1+2\sqrt{-5})$ is not an irreducible.
Then, $21 = N(1+2\sqrt{-5}) = N(\beta)N(\gamma)$.
However, we know that the integer factors of $21$ are $1,3,7,21$.
Without loss of generality, we have $N(\beta) = 3$ which is not possible.
Thus, $1+2\sqrt{-5}$ is an irreducible.\\

However neither $3$ nor $7$ is an associate of $1+2\sqrt{-5}$.
Since $|N(1+2\sqrt{-5})| \ne N(3)$ and $N(1+2\sqrt{-5}) \ne N(7)$.
Clearly, the factorisation of $21 \in \mathbb{Z}[\sqrt{-5}]$ is not unique.
Therefore, $\mathbb{Z}[\sqrt{-5}]$ is not a UFD.
\end{proof}
\subsubsection{Fermat's $p = a^2+b^2$ theorem}
\begin{theorem}[Fermat]
	Let $p$ be an odd prime integer.
	Then $p = a^2 + b^2$ where $a,b \in \mathbb{Z}$ if and only if $p \cong 1 \pmod{4}$
\end{theorem}
\begin{proof}
	Suppose there exists an odd prime $p$ such that $p = a^2 + b^2$.
	Then $a,b$ are of different parity.
	Without loss of generality, $a$ is even and $b$ is odd.
	Let $a=2r$ and $b=2s+1$.
	Then $a^2+b^2 = 4r^2 + 4s^2 + 1 \cong 1 \pmod{4}$.\\

	Suppose $p \cong 1 \pmod{4}$.
	Then $\mathbb{Z}_p$ is a cyclic group of order $p-1$ which has a element $n$ of order $4$ since $4|(p-1)$.
	Then $n^2 = -1 \in \mathbb{Z}_p$.
	And $n^2+1 \cong 0 \pmod{p}$.
	In other words, $p | (n^2+1)$.\\

	We claim that, $p$ is not an irreducible in $\mathbb{Z}[i]$.
	Suppose $p$ is an irreducible then $p|(n^2+1) \implies p|(n+i)$ or $p|(n-i)$.
	And $p|(n+i) \implies n+i = p(a+bi) \implies n= pa \text{ and }1 = pb$.
	But, $1=pb$ is not possible.
	Similarly, $p|(n-i) \implies n-i = p(a+bi) \implies -1 = pb$ is also not possible.
	Thus if $p \cong 1 \pmod{4}$, then $p$ is not an irreducible in $\mathbb{Z}[i]$.\\

	Since $p$ is not an irreducible in $\mathbb{Z}[i]$.
	$p = (a+bi)(c+di)$ where $a+bi,c+di$ are non-units in $\mathbb{Z}[i]$.
	Considering the Gaussian norm $N$ on $\mathbb{Z}[i]$ defined by $N(a+bi) = a^2 + b^2$.
	We have, $p^2 = N(p) = N(a+bi)N(c+di) = (a^2+b^2)(c^2+d^2)$.
	And $N((a+bi) \ne 1$ since for Gaussian norm $N(\alpha) = 1 \iff \alpha = 1$.
	Similarly, $N(c+di) \ne 1$.
	Therefore, without loss of generality $N(a+bi) = p$ since $a^2+b^2 > 0$.
	In other words, $p = a^2 + b^2$.
\end{proof}
\subsection{Exercise \S47}
\begin{enumerate}
	\item We have $5$ is an odd prime and  $5 \cong 1 \mod{4}$.
		Therefore $5$ is not an irreducible Gaussian integer.
		Clearly, $2^2+1^2 = 5 \implies (2+i)(2-i) = 5$.\\

		And $N(2+i) = 5$ is a prime, thus $2+i$ is an irreducible.
		Similarly, $2-i$ is also an irreducible.
		Therefore $5 = (2+i)(2-i)$ is factorisation using irreducibles Gaussian integers.
		(hint : $2^2+1^ = 5$. But, $1 \ast 1 + 2 \ast 2 = 5$)\\

		Note : We have $ 5 = (2+i)(2-i) = (1+2i)(1-2i)$.
		However $5$ has a unique factorisation since $(2+i)$ and $(1-2i)$ are associates $(2+i)(0-i) = 1-2i$ where $-i \in \mathbb{Z}[i]$ is a unit with multiplicative inverse $i$.

	\item We have $7$ is an odd prime.
		However $7 \cong 3 \pmod{4}$.
		Therefore $7$ is an irreducible Gaussian integer.
	\item We have $N(4+3i) = 25$.
		Clearly, $(4+3i) = \alpha\beta \implies N(\alpha) = N(\beta) = 5$.
		Therefore, $4+3i = (2-i)(1+2i)$ is a factorisation of $4+3i$.
		(Hint : $2^2+1^2 = 5$. But, $1 \ast 2 + 1 \ast 2 = 4$.)
	\item We have $N(6-7i) = 85 = 5 \ast 17$.
		Clearly $6-7i = (2+i)(1-4i)$.
		(Hint : $2^2+1^2 = 5$ and $4^2+1^2 = 17$. But $1 \ast 2 + 1 \ast 4 = 6$.)
	\item We have $6 = 2 \ast 3$ in $\mathbb{Z}[\sqrt{-5}]$.
		Then, $N(\alpha\beta) = 4 \implies a^2+5b^2 = 2$ is not possible.
		And, $N(\alpha\beta)= 9 \implies a^2+5b^2 = 3$ is also not possible. Therefore, $6 = 2 \ast 3$ is a factoriation in $\mathbb{Z}[\sqrt{-5}]$.\\

		However $N(\alpha\beta) = 6 \implies a^2 + 5b^2 = 6 \implies |a| = |b| = 1$.
		Clearly, $6 = (1-\sqrt{-5})(1+\sqrt{-5})$ is another factorisation.
\end{enumerate}
%Module 3
\pagebreak
{\Large Module 3 Field Automorphisms}
\section{Automorphism and Fields \S48}
\subsubsection*{Context}
\begin{enumerate}
	\item Let $F$ be a field.
		Then there exists a unique field $\bar{F}$ which is algebraically closed.
	\item Let $F$ be a field.
		Let $\alpha$ be algebraic over $F$.
		Then there exists a unique, monic, irreducible, minimal polynomial $irr(\alpha,F) = p(x) \in F[x]$ such that $p(\alpha) = 0$.
	\item $F(\alpha)$ is a vector space of dimension $[F(\alpha) : F] = \deg (\alpha,F)$ over $F$.
\end{enumerate}

\subsection{Conjugation Isomorphisms}
\begin{definition}[conjugates]
	Let $E$ be an algebraic extension of $F$.
	Let $\alpha,\beta \in E$.
	Then $\alpha$ and $\beta$ are \textbf{conjugates over $F$} if $irr(\alpha,F) = irr(\beta,F)$.
\end{definition}
\hrule\vspace{1em}
For example, $i,-i$ are conjugates over $\mathbb{R}$.
$irr(i,\mathbb{R}) = x^2+1 = irr(-i,\mathbb{R})$.
\hrule\vspace{1em}
\begin{theorem}[conjugation isomorphism]
	Let $F$ be a field.
	Let $\alpha,\beta$ be algebraic over $F$ with $\deg(\alpha,F) = n$.
	The map $\psi_{\alpha,\beta} : F(\alpha) \to F(\beta)$ defined by 
	\[ \psi_{\alpha,\beta} \left( c_0 + c_1\alpha + \dots + c_{n-1}\alpha^{n-1} \right) = c_0 + c_1\beta + \dots + c_{n-1}\beta^{n-1} \]
	where $c_j \in F$ is an isomorphism from $F(\alpha)$ onto $F(\beta)$ if and only if $\alpha,\beta$ are conjugates over $F$.
\end{theorem}
\begin{proof} 
	Let $\psi_{\alpha,\beta} : F(\alpha) \to F(\beta)$ be an isomorphism.
	Let $\deg(\alpha,F) = n$ and $irr(\alpha,F) = q(x)$ given by
	\[ irr(\alpha,F) = q(x) = a_0 + a_1 x + \dots + a_n x^n \]
	Then 
	\[ a_0 + a_1 \alpha + \dots + a_n \alpha^n = 0 \]
	Thus,
	\[ \psi_{\alpha,\beta}(0) = \psi_{\alpha,\beta} (a_0 + a_1 \alpha + \dots + a_n \alpha^n) = a_0 + a_1 \beta + \dots + a_n \beta^n = 0 \]
	Let $irr(\beta,F) = p(x) \in F[x]$.
	Then, $p(\beta) = 0$.
	We already have, $q(\beta) = 0$.
	Let $\phi_\beta : F[x] \to F(\beta)$ be evaluation homomorphism.
	Then, $\phi_\beta(q(x)) = q(\beta)$.
	Therefore, $q(x) \in \ker(\phi_\beta)$
	However, $\ker(\phi_\beta)$ is the ideal generated by $p(x)$.
	Therefore, $p(x)$ must divide $q(x)$ in $F[x]$.
	Thus, $irr(\beta,F)$ divides $irr(\alpha,F)$.\\

	Similarly, $\psi_{\alpha,\beta}^{-1} : F(\beta) \to F(\alpha)$ is an isomorphism and $irr(\alpha,F)$ divides $irr(\beta,F)$.
	We know that, both the polynomials are monic polynomials.
	Therefore, $irr(\alpha,F) = irr(\beta,F)$.
	That is, $\alpha,\beta$ are conjugates over $F$.\\

	\hrule\vspace{1em}

	Let $irr(\alpha,F) = irr(\beta,F) = p(x)$.
	Let $\phi_\alpha : F[x] \to F(\alpha)$ and $\phi_\beta : F[x] \to F(\beta)$ be evaluation homomorphisms.
	We know that for any polynomial $f(x) \in F[x]$ with $f(\alpha) = 0$, $p(x)$ divides $f(x)$.
	Thus, $\ker(\phi_\alpha) = \generator{p(x)}$.
	Similarly, $\ker(\phi_\beta) = \generator{p(x)}$.\\

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\draw (2,3) node {$F[x]$};
		\draw (2,0) node {$F[x]/\generator{p(x)}$};
		\draw (-2,0) node {$F(\alpha)$};
		\draw (6,0) node {$F(\beta)$};
		\draw[-latex] (2,2.8) -- node(e1)[label=right:$\gamma$]{} (2,0.2);
		\draw[-latex] (1.8,2.8) -- node(e2)[label=left:$\phi_\alpha$]{} (-1.6,0.4);
		\draw[-latex] (2.2,2.8) -- node(e3)[label=right:$\phi_\beta$]{} (5.6,0.4);
		\draw[-latex] (0.8,0) -- node(e4)[label=above:$\psi_\alpha$]{} (-1.4,0);
		\draw[-latex] (3.2,0) -- node(e5)[label=above:$\psi_\beta$]{} (5.4,0);
	\end{tikzpicture}
	\caption{$\psi_{\alpha,\beta} = \psi_\beta \circ \psi_\alpha^{-1}$}
\end{figure}

	By fundamental homomorphism theorem, there exists a canonical isomorphism 
	\[ \psi_\alpha : F[x]/\generator{p(x)} \to \phi_\alpha[F[x]],\quad \psi_\alpha(r(x) + \generator{p(x)}) = \phi_\alpha(r(x)) = r(\alpha) \]
	Similary, there exists another canonical isomorphism
	\[ \psi_\beta : F[x]/\generator{p(x)} \to \phi_\beta[F[x]],\quad \psi_\beta(r(x) + \generator{p(x)} = \phi_\beta(r(x)) = r(\beta) \]
	Therefore, $\psi_{\alpha,\beta} = \psi_\beta \circ \psi_\alpha^{-1} : F(\alpha) \to F(\beta)$ is an isomorphism such that
	\[ \psi_\beta \circ \psi_\alpha^{-1} (c_0 + c_1 \alpha + \dots +c_{n-1}\alpha^{n-1}) = c_0 + c_1 \beta + \dots + c_{n-1} \beta^{n-1} \]
\end{proof}

\begin{commentary}
\begin{challenge}
	No algebraic number over $\mathbb{R}$ has multiple conjugates.(proved later)
	However, there exists fields over which there exists algebraic numbers with multiple conjugates.
\end{challenge}
\begin{proof}
	Let $F = \mathbb{Z}_2$.
	Polynomial $x^3+x+1$ is an irreducible over $\mathbb{Z}_2$ since $\phi_0(x^3+x+1) = 0^3+0+1 \ne 0$ and $\phi_1(x^3+x+1) = 1^3+1+1 \ne 0$.
	Let $\alpha$ be a zero of $x^3+x+1$.
	Then $\alpha$ is algebraic over $\mathbb{Z}_2$.
	And $\phi_\alpha(x^3+x+1) = \alpha^3+\alpha+1 = 0$.
	Then $\alpha$ has two conjugates $\beta,\gamma$.\\

	We have, $[\mathbb{Z}(\alpha):\mathbb{Z}_2] = 3$.
	Thus, $|\mathbb{Z}(\alpha)| = 8$.
	And $\mathbb{Z}_2(\alpha) = \{ 0,1,\alpha,\alpha^2,\alpha+\alpha^2,1+\alpha,1+\alpha^2,1+\alpha+\alpha^2 \}$.
	Clearly, $\alpha^3 = \alpha+1$.
	We can test each element of $\mathbb{Z}_2(\alpha)$ to find other zeroes of the polynomial $x^3+x+1$.
	Thus, $\phi_{\alpha^2} = 0$ and $\phi_{\alpha+\alpha^2} = 0$.
	Let $\beta = \alpha^2$ and $\gamma = \alpha+\beta$.\\

	Now the we have conjugate isomorphisms $\psi_{\alpha,\beta} : \mathbb{Z}_2(\alpha) \to \mathbb{Z}_2(\beta)$ and $\psi_{\alpha,\gamma} : \mathbb{Z}_2(\alpha) \to \mathbb{Z}_2(\gamma)$ defined by

\begin{figure}[h]
	\centering
	\begin{tikzpicture}
		\draw (-2,0) node {$0$};
		\draw (-2,1) node {$1$};
		\draw (-2,2) node {$\alpha$};
		\draw (-2,3) node {$\alpha^2$};
		\draw (-2,4) node {$\alpha+1$};
		\draw (-2,5) node {$\alpha^2+1$};
		\draw (-2,6) node {$\alpha^2+\alpha$};
		\draw (-2,7) node {$\alpha^2+\alpha+1$};
		\draw (2,0) node {$0$};
		\draw (2,1) node {$1$};
		\draw (2,2) node {$\beta^2+\beta$};
		\draw (2,3) node {$\beta$};
		\draw (2,4) node {$\beta^2+\beta+1$};
		\draw (2,5) node {$\beta+1$};
		\draw (2,6) node {$\beta^2$};
		\draw (2,7) node {$\beta^2+1$};
		\draw[-latex,black] (-2,8) -- node(e1)[label=above:$\psi_{\alpha,\beta}$]{} (2,8);
		\draw[-latex,black] (-1.5,0) -- (1.5,0);
		\draw[-latex,black] (-1.5,1) -- (1.5,1);
		\draw[-latex,black] (-1.5,2) -- (1.5,3);
		\draw[-latex,black] (-1.5,3) -- (1.5,6);
		\draw[-latex,black] (-1.3,4) -- (1.3,5);
		\draw[-latex,black] (-1.3,5) -- (1.3,7);
		\draw[-latex,black] (-1.3,6) -- (1.3,2);
		\draw[-latex,black] (-1,7) -- (1,4);
		\draw[-latex,blue] (2,8) -- node(e2)[label=above:$\psi_{\beta,\gamma}$]{} (6,8);
		\draw[-latex,blue] (2.5,0) -- (5.5,0);
		\draw[-latex,blue] (2.5,1) -- (5.5,1);
		\draw[-latex,blue] (2.8,2) -- (5.3,3);
		\draw[-latex,blue] (2.5,3) -- (5.5,6);
		\draw[-latex,blue] (3,4) -- (5,5);
		\draw[-latex,blue] (2.8,5) -- (5.5,7);
		\draw[-latex,blue] (2.5,6) -- (5.5,2);
		\draw[-latex,blue] (3,7) -- (5.3,4);
		\draw (6,0) node {$0$};
		\draw (6,1) node {$1$};
		\draw (6,2) node {$\gamma^2$};
		\draw (6,3) node {$\gamma^2+\gamma$};
		\draw (6,4) node {$\gamma^2+1$};
		\draw (6,5) node {$\gamma^2+\gamma+1$};
		\draw (6,6) node {$\gamma$};
		\draw (6,7) node {$\gamma+1$};
		\draw (10,0) node {$0$};
		\draw (10,1) node {$1$};
		\draw (10,2) node {$\alpha$};
		\draw (10,3) node {$\alpha^2$};
		\draw (10,4) node {$\alpha+1$};
		\draw (10,5) node {$\alpha^2+1$};
		\draw (10,6) node {$\alpha^2+\alpha$};
		\draw (10,7) node {$\alpha^2+\alpha+1$};
		\draw[-latex,black] (6,8) -- node(e3)[label=above:$\psi_{\gamma,\alpha}$]{} (10,8);
		\draw[-latex,black] (6.5,0) -- (9.5,0);
		\draw[-latex,black] (6.5,1) -- (9.5,1);
		\draw[-latex,black] (6.5,2) -- (9.5,3);
		\draw[-latex,black] (6.8,3) -- (9.3,6);
		\draw[-latex,black] (6.8,4) -- (9.3,5);
		\draw[-latex,black] (7,5) -- (9,7);
		\draw[-latex,black] (6.5,6) -- (9.5,2);
		\draw[-latex,black] (6.8,7) -- (9.3,4);
	\end{tikzpicture}
	\caption{$\psi_{\alpha,\beta} : \mathbb{Z}_2(\alpha) \to \mathbb{Z}_2(\beta)$, $\psi_{\beta,\gamma} : \mathbb{Z}_2(\beta) \to \mathbb{Z}_2(\gamma)$, $\psi_{\gamma,\alpha} : \mathbb{Z}_2(\gamma) : \mathbb{Z}_2(\alpha)$.}
\end{figure}
Clearly, there are 6 conjugate isomorphisms on $\mathbb{Z}_2(\alpha)$.
However, only two of them are distinct.
\end{proof}
\end{commentary}

\begin{corollary}
	Let $\alpha$ be algebraic over $F$.
	Let $E \le \bar{F}$.
	Then every isomorphism $\psi : F(\alpha) \to E$ with $\psi(a) = a,\ \forall a \in F$ maps $\alpha$ into its conjugate over $F$.
	And for any conjugate $\beta$ of $\alpha$ over $F$, there exists a unique isomorphism $\psi_{\alpha,\beta} : F(\alpha) \to \bar{F}$ such that $\psi_{\alpha,\beta}(\alpha) = \beta$ and $\forall a \in F,\ \psi_{\alpha,\beta}(a) = a$.
\end{corollary}
\begin{proof} 
	Let $\psi : F(\alpha) \to E$ be an isomorphism such that $\psi(a) = a,\ \forall a \in F$.
	Let $irr(\alpha,F) = p(x) = a_0 + a_1x + \dots + a_nx^n$.
	Then $\phi_\alpha(p(x)) = p(\alpha) = a_0 + a_1\alpha + \dots + a_n \alpha^n = 0$.
	And, $\psi(0) = \psi(p(\alpha)) = a_0 + a_1 \psi(\alpha) + \dots + a_n \psi(\alpha)^n = 0$.
	That is, $\psi(\alpha)$ is a zero of the polynomial $p(x)$.
	Thus, $\alpha,\psi(\alpha)$ are conjugates over $F$.\\

	\hrule\vspace{1em}

	Let $\alpha,\beta$ be conjugates over $F$.
	Then, the conjugation isomorphism $\psi_{\alpha,\beta} : F(\alpha) \to F(\beta)$ defined by
	\[ \psi_{\alpha,\beta}(a_0 + a_1\alpha + \dots + a_{n-1} \alpha^{n-1}) = a_0 + a_1 \beta + \dots + a_{n-1} \beta^{n-1} \]
	is an isomorphism which maps $a \to a,\ \forall a \in F$ and $\alpha \to \beta$.
	Since every element in $F(\alpha)$ is of the form $a_0 + a_1 \alpha + \dots + a_{n-1}\alpha^{n-1}$.
	And the definition $a \to a,\ \alpha \to \beta$ compltelely determines the isomorphism.
	Therefore, there exists a unique conjugate isomorphism which maps $\alpha$ to its conjugate $\beta$.
\end{proof} 

\begin{corollary}
	Let $f(x) \in \mathbb{R}[x]$.
	Let $a+ib \in \mathbb{C}$.
	If $f(a+ib) = 0$, then $f(a-ib) = 0$.
	Also, complex zeroes of polynomials with real-coefficients occur in conjugate pairs.
\end{corollary}
\begin{important}
	In other words, complex conjugates are conjugates over $\mathbb{R}$.
\end{important}
\begin{proof} 
	We have $\mathbb{C} = \mathbb{R}(i)$ where $i$ is algebraic over $\mathbb{R}$, $irr(i,\mathbb{R}) = x^2+1$.
	Clearly, $i,-i$ are conjugates over $\mathbb{R}$.
	And $\psi_{i,-i} : \mathbb{C} \to \mathbb{C}$ is a conjugate isomorphism which maps $a+ib \to a-ib$.\\

	Let $a+ib \in \mathbb{C}$.
	Let $f(x) \in \mathbb{R}[x]$ such that $irr(a+ib,\mathbb{R}) = f(x)$.\\
	Since $f(x) \in \mathbb{R}[x]$,
	\[ f(x) = c_0 + c_1x+ \dots c_nx^n \]
	Since $irr(a+ib,\mathbb{R}) = f(x)$,
	\[ \phi_{a+ib}(f(x)) = f(a+ib) = c_0 + c_1(a+ib) + \dots + c_n(a+ib)^n = 0 \]
	Field $\mathbb{R}$ is fixed under the conjugate isomorphism, $\psi_{i,-i}$.
	Thus, $\psi_{i,-i}(0) = 0$,
	\[ \psi_{i,-i}(0) = \psi_{i,-i}(f(a+ib)) = f(a-ib) = c_0 + c_1(a-ib) + \dots + c_n(a-ib)^n = 0 \]
	Therefore, $(a-ib)$ is a zero of $f(x)$.
	Let $irr(a-ib,\mathbb{R}) = p(x)$.
	Then $f(x) \in \generator{p(x)}$.
	That is, $p(x)$ divides $f(x)$.
	Similarly, $\psi_{-i,i}(p(a-ib)) = p(a+ib) = 0$.
	And $f(x)$ divides $p(x)$.
	Therefore, $irr(a-ib,\mathbb{R}) = p(x) = f(x) = irr(a+ib,\mathbb{R})$.
	Clearly, $a+ib,a-ib$ are conjugates over $\mathbb{R}$.\\
	
	Let $w = c+id \in \mathbb{C}$ be another conjugate of $z=a+ib$ where $a,b,c,d \in \mathbb{R}$.
	Suppose $\psi_{z,w} : \mathbb{C} \to \mathbb{C}$ is a conjugation isomorphism.
	If $a+ib$ is a zero of some $g(x) \in \mathbb{R}[x]$.
	Then $c+id$ is also a zero of $g(x)$ by conjugation isomorphism.
	We have, $\psi_{z,w}(a) = a, \psi_{z,w}(b) = b$ since $a,b \in \mathbb{R}$.
	Thus, $\psi_{z,w}(a+ib) = \psi_{z,w}(a) + \psi_{z,w}(i)\psi_{z,w}(b) = a+\psi_{z,w}(i)b = c+id$.
	Clearly, $\psi_{z,w}(i) = \frac{c-a}{b} + i\frac{d}{b}$.
	Thus, $a=c$ and $d = \pm b$ since $i,-i$ are the only zero of $x^2+1$.
	Therefore, conjuates over $\mathbb{R}$ occur in pairs.
\end{proof} 

\begin{commentary}
\begin{remark}
	The notion of complex conjugates
	\begin{enumerate}
		\item Complex conjugates $z,\bar{z}$ are conjugates over the real field $\mathbb{R}$ with irreducible, monic polynomial $irr(z,\mathbb{R}) = (x-\Re{(z)})^2+\Im{(z)}^2$.
		\item Any non-real number, $z \notin \mathbb{R}$ which is algebraic over $\mathbb{R}$ has a unique conjugate $\bar{z}$ over $\mathbb{R}$.
	\end{enumerate}
\end{remark}
\end{commentary}

\begin{remark}
	$\sqrt{2},-\sqrt{2}$ are conjugates over $\mathbb{Q}$ with $irr(\sqrt{2},\mathbb{Q}) = x^2-2$.
	Thus, $\psi_{\sqrt{2},-\sqrt{2}} : \mathbb{Q}(\sqrt{2}) \to \mathbb{Q}(\sqrt{2})$ is a conjugation isomorphism.
	Elements of $\mathbb{Q}(\sqrt{2})$ are of the form $a+\sqrt{2}b$ where $a,b \in \mathbb{Q}$.
	Clearly, $\psi_{\sqrt{2},-\sqrt{2}}(a+\sqrt{2}b) = a-\sqrt{2}b$.
\end{remark}
\begin{commentary}
	Result : 
	If $\sqrt{2}$ is a zero of a polynomial with rational coefficients, then $-\sqrt{2}$ is also a zero of it.
	Therefore, $\sqrt{2}$ is an eigen value of a rational matrix, if and only if $-\sqrt{2}$ is also an eigen value of it.
	Similarly, $a+ib$ is an eigen value of a real matrix, if and only if $a-ib$ is also an eigen value of it.
\end{commentary}
\subsection{Automorphism and Fixed Fields}
\begin{definition}[automorphism]
	Automorphism of a field is an isomorphism of a field onto itself.
\end{definition}
\begin{definition}[fixed]
	Let $\sigma : F \to F$ be a field automorphism.
	The set $S = \{ a \in F : \sigma(a) = a \}$ of elements invariant under $\sigma$ is fixed under $\sigma$.
	Let $E$ be  a subfield of $F$ such that $\forall a \in E, \sigma(a) = a$.
	Then $E$ is left fixed by $\sigma$.
\end{definition}
\hrule \vspace{1em}
For example, the conjugation map $\psi_{\sqrt{3},-\sqrt{3}} : \mathbb{Q}(\sqrt{2},\sqrt{3}) \to \mathbb{Q}(\sqrt{2},\sqrt{3})$ leaves $\mathbb{Q}(\sqrt{2})$ fixed.\\

\begin{commentary}
	We have, $irr(\sqrt{2},\mathbb{Q}) = x^2-2$.
	Elements of $\mathbb{Q}(\sqrt{2})$ are of the form $a+b\sqrt{2}$ where $a,b \in \mathbb{Q}$.
	\[ \mathbb{Q}(\sqrt{2},\sqrt{3}) = \mathbb{Q}(\sqrt{2})(\sqrt{3}) \]
	And $irr(\sqrt{3},\mathbb{Q}(\sqrt{2})) = x^2 -3$.
	Thus, elements of $\mathbb{Q}(\sqrt{2})(\sqrt{3})$ are of the form $x+y\sqrt{3}$ where $x,y \in \mathbb{Q}(\sqrt{2})$.
	\[ \left( a+b\sqrt{2} \right) + \left( c+d\sqrt{2} \right)\sqrt{3} = a+b\sqrt{2}+c\sqrt{3}+d\sqrt{6} \]
\end{commentary}
Elements of $\mathbb{Q}(\sqrt{2},\sqrt{3})$ are of the form $a+b\sqrt{2} + c\sqrt{3}+ d\sqrt{6}$ where $a,b,c,d \in \mathbb{Q}$.
\[ \psi_{\sqrt{3},-\sqrt{3}} \left( a+b\sqrt{2}+c\sqrt{3}+d\sqrt{6} \right) = a+b\sqrt{2}-c\sqrt{3}-d\sqrt{2}\sqrt{3} \]
Thus, an element of $\mathbb{Q}(\sqrt{2},\sqrt{3})$ is left fixed by $\psi_{\sqrt{3},-\sqrt{3}}$ if and only if $c,d = 0$.
\hrule \vspace{1em}
\begin{theorem}
	Let $\{ \sigma_i : i \in I \}$ be a collection of automorphisms of field $E$.
	Then, the $\displaystyle E_{\{\sigma_i\}} = \left\{ a \in E : \sigma_i(a) = a, \forall i \in I \right\}$ is a subfield of $E$.
\end{theorem}
\begin{important}
	The set fixed by an automorphism of a field is a \textbf{subfield}.\\
\end{important}
\begin{commentary}
	Quick Revision : How to test whehter $F$ is a subfield of field $E$ ?
	\begin{enumerate}
		\item Preservation of identitites, $0,1 \in F$ (usually trivial)
		\item Closure of binary operations, $\forall a,b \in F,\ a\pm b, ab \in F$ (hard to prove)
		\item Existence of inverses (easy to prove)
			\begin{enumerate}
				\item $\forall a \in F,\ -a \in F$
				\item $\forall a \in F,\ (a \ne 0), a^{-1} \in F$.
			\end{enumerate}
	\end{enumerate}
\end{commentary}
\begin{proof} 
	Let $a,b \in E_{\{\sigma_i\}}$.
	Then $\sigma_i(a) = a,\ \forall i \in I$ and $\sigma_i(b) = b,\ \forall i \in I$.
	Since $\sigma_i$'s are homomorpisms on $E$,
	\[ \sigma_i(a \pm b) = \sigma_i(a) \pm \sigma_i(b) = a \pm b \]
	\[ \sigma_i(ab) = \sigma_i(a)\sigma_i(b) = ab \]
	Thus, $a,b \in E_{\{\sigma_i\}} \implies a \pm b, ab \in E_{\{\sigma_i\}}$.\\

	We have, $\sigma_i$'s are automorphisms.
	Thus, $\sigma_i(0) = 0$ and $\sigma_i(1) = 1$ for every $i \in I$.
	We have, $\sigma_i(0) = 0$.
	\[ 0 = \sigma_i(0) = \sigma_i(a+(-a)) = \sigma_i(a) + \sigma_i(-a) = a -\sigma_i(a) \]
	Thus, $\sigma_i(-a) = -a,\ \forall i \in I$.
	And, $\forall a \in E_{\{\sigma_i\}},\ -a \in E_{\{\sigma_i\}}$.	\\
	Similarly, $\sigma_i(1) =1$.
	Let $a \ne 0$.
	\[ 1 = \sigma_i(1) = \sigma_i(aa^{-1}) = \sigma_i(a) \sigma_i(a^{-1}) = a\sigma_i(a^{-1}) \]
	Thus, $\sigma_i(a^{-1}) = a^{-1},\ \forall i \in I$.
	And,  $\forall a \in E_{\{\sigma_i\}},\ (a \ne 0),\ a^{-1} \in E_{\{\sigma_i\}}$.
	Therefore, $E_{\{\sigma_i\}}$ is a subfield of $E$.
\end{proof} 

\begin{definition}
	Let $\sigma$ be an automorphism on field $E$.
	Then $E_{\{\sigma\}}$ is the subfield left fixed by $\sigma$.
\end{definition}
\hrule \vspace{1em}
For example, we have seen earlier that the subfield left fixed by the conjugation isomorphism 
\[ \psi_{\sqrt{3},-\sqrt{3}} : \mathbb{Q}\left(\sqrt{2},\sqrt{3}\right) \to \mathbb{Q}\left(\sqrt{2},\sqrt{3}\right)\]
is $\mathbb{Q}\left(\sqrt{2}\right)$.
Therefore,
\[ \mathbb{Q} \left( \sqrt{2},\sqrt{3} \right)_{\left\{ \psi_{\sqrt{3},-\sqrt{3})}\right\}} = \mathbb{Q}\left(\sqrt{2}\right) \]

\begin{commentary}
	Here, $E = \mathbb{Q}\left(\sqrt{2},\sqrt{3}\right)$ and $\sigma = \psi_{\sqrt{3},-\sqrt{3}}$ and $E_{\{\sigma\}} = \mathbb{Q}\left( \sqrt{2} \right)$.
\end{commentary}
\hrule \vspace{1em}
\begin{theorem}
	The set of all automorphisms of a field $E$ is a group under function composition.
\end{theorem}
\begin{proof} 
	Let $E$ be a field.
	Let $S_E$ be the set of all permutations on the field $E$.
	Clearly, the field permuations are associative under function composition.\\

	We have, identity permutation $i : E \to E$ is an automorphism of $E$.
	Let $\sigma$ be any automorphisms of $E$.
	Then, we have 
	\[ i \circ \sigma = \sigma = \sigma \circ i \]
	We have $\sigma$ is a permutation on $E$.
	Let $\sigma^{-1}$ be the inverse permutation of $\sigma$.
	Clearly, $\sigma^{-1} : E \to E$ is also an automorphism.
	And,
	\[ \sigma \circ \sigma^{-1} = i = \sigma^{-1} \circ \sigma \]
	Let $\tau$ be an automorphism on $E$.
	Then $\sigma \circ \tau$ is an automorphism on $E$.
	Thus, set of all automorphisms on $E$ is a subgroup of permuation group $S_E$.
\end{proof} 

\begin{theorem}
	Let $E$ be a field and $F$ be a subfield of $E$.
	Then the set of all automorphisms of $E$ leaving $F$ fixed, say $G(E/F)$ is a subgroup of the set of all automorphisms on $E$.
	Furthermore, $F \le E_{G(E/F)}$.
\end{theorem}
\begin{proof} 
	Let $\sigma,\tau \in G(E/F)$.
	We have $\sigma(a) = a$ and $\tau(a) = a$ for every $a \in F$.
	Thus, $(\sigma \circ \tau)(a) = \sigma(\tau(a)) = \sigma(a) = a$.
	Therefore, $\sigma \circ \tau \in G(E/F)$.\\

	We have, $\sigma(a) = a \implies a = \sigma^{-1}(a),\ \forall a \in F$.
	Thus, $\sigma^{-1} \in G(E/F)$.	
	Therefore, $G(E/F)$ is a subgroup of all automorphisms on $E$.\\

	The subfield $E_{G(E/F)}$ is the set of all automorphims on $E$ leaving $F$ fixed.
	Let $\sigma \in G(E/F)$.
	Then, 
	\[ a \in F \implies \sigma(a) = a \implies a \in E_{\{\sigma\}} \implies a \in E_{G(E/F)} \]
	Thus, subfield $F$ is contained in $E_{G(E/F)}$.
\end{proof} 

\begin{definition}
	Let $F$ be a subfield of a field $E$.
	The group of $E$ over $F$, $G(E/F)$ is the set of all automorphisms on $E$ leaving $F$ fixed.
\end{definition}

\begin{important}
	Any automorphism on field $E$ leaves the prime field $\mathbb{Q}$ or $\mathbb{Z}_p$ fixed.
\end{important}
\hrule \vspace{1em}
For example, consider the set of all automorphisms on $\mathbb{Q}\left(\sqrt{2},\sqrt{3}\right)$ (leaving $\mathbb{Q}$ fixed.)
We have, 
\[ i,\quad \psi_{\sqrt{2},-\sqrt{2}},\quad \psi_{\sqrt{3},-\sqrt{3}},\quad \psi_{\sqrt{2},-\sqrt{2}} \circ \psi_{\sqrt{3},-\sqrt{3}} \]
are the only automorphisms on $\mathbb{Q}\left(\sqrt{2},\sqrt{3}\right)$.
Therefore, we have 
\[ G\left(\mathbb{Q}(\sqrt{2},\sqrt{3})/\mathbb{Q}\right) \simeq V \simeq \mathbb{Z}_2 \times \mathbb{Z}_2 \]
since each automorphism is an inverse of itself.
Also we have, $[\mathbb{Q}(\sqrt{2},\sqrt{3}) : \mathbb{Q}] = 4$ is the order of the group $G(\mathbb{Q}(\sqrt{2},\sqrt{3})/\mathbb{Q})$.\\

\begin{commentary}
	Earlier we have seen, $\mathbb{Z}_2(\alpha)$ where $irr(\alpha,\mathbb{Z}_2) = x^3+x+1$.
	The conjugates of $\alpha$ over $\mathbb{Z}_2$ are $\beta, \gamma$.
	However, the distinct automorphisms are,
	\[ i,\quad \psi_{\alpha,\beta},\quad \psi_{\beta,\alpha} \]
	Therefore,
	\[ G\left( \mathbb{Z}_2(\alpha),\mathbb{Z}_2 \right) \simeq \mathbb{Z}_3 \qquad \text{ since } \psi_{\alpha,\beta} \circ \psi_{\beta,\alpha} = i \]
	Once again, $[\mathbb{Z}_2(\alpha) : \mathbb{Z}_2] = 3 = |G(\mathbb{Z}_2(\alpha)/\mathbb{Z}_2)|$ makes our task much easier.
\end{commentary}
\hrule \vspace{1em}
\subsection{Frobenius Automorphism}
\begin{theorem}[Frobeinus Automorphism]
	Let $F$ be a finite field of characteristic $p$.
	Then the map $\sigma_p : F \to F$ defined by $\sigma_p(a) = a^p,\ \forall a\in F$ is an automorphism on $F$.
	Also $F_{\{\sigma_p\}} \simeq \mathbb{Z}_p$.
\end{theorem}
\begin{proof} 
	Let $a,b \in F$.
	Then
	\[ \sigma_p(a+b) = (a+b)^p = a^p + b^p = \sigma_p(a) + \sigma_p(b)\]
	\[ \sigma_p(ab) = (ab)^p = a^p b^p = \sigma_p(a) \sigma_p(b) \]
	Thus, $\sigma_p$ is a homomorphism.\\

	We have,
	\[ \sigma_p(a) = 0 \implies a^p = 0 \implies a = 0 \]
	Thus, $\ker(\sigma_p) = \{ 0 \}$.
	Therefore, $\sigma_p$ is injective.\\

	Since $F$ is finite and $\sigma_p : F \to F$, $\sigma_p$ is surjective.
	Therefore, $\sigma_p$ is an automorphism on $F$.\\

	We have, $F$ is of characteristics $p$.
	And $\sigma_p(1) = 1^p = 1$.
	Let $\mathbb{Z}_p$ be the prime field contained in $F$.
	Then, $\forall c \in \mathbb{Z}_p,\ \sigma_p(c) = c^p = c$.
	Therefore, $\mathbb{Z}_p$ is fixed by $\sigma_p$.\\

	The polynomial $x^p-x$ has at most $p$ zeroes.
	Thus, it doesn't have any zero other than elements of the prime subfield of $F$.
	\[ a \in F_{\{\sigma_p\}} \iff \sigma_p(a) = a \iff a^p = a \iff a^p - a = 0  \iff \phi_a(x^p-x) = 0 \]
	Therefore, $F_{\{\sigma_p\}} \simeq \mathbb{Z}_p$.
\end{proof} 
\subsection{Exercises \S48}
\begin{enumerate}
	\item
	%\setcounter{enumi}{27}
	%\item Consider $\sigma_p : \bar{\mathbb{Z}}_p \to \bar{\mathbb{Z}}_p$ defined by $\sigma_p(a) = a^p$.
	%	Let $\alpha$ be a zero of $x^p-x-1 \in \mathbb{Z}_p[x]$.
	%	Then $\alpha^p = \alpha + 1$.
	%	And $(\alpha^p)^p = (\alpha+1)^p = \alpha^p + 1 = \alpha + 2$.
	%	Continuing like this we get, $\alpha \to \alpha+1 \to \alpha+2 \to \dots $,
\end{enumerate}

\section{The Isomorphism Extension Theorem \S49}
\subsection{Extension Theorem}
\begin{theorem}[isomorphism extension]
	Let $E$ be an algebraic extension of field $F$.
	Let $\sigma$ be an isomorphism on $F$ onto $F'$.
	Let $\bar{F}'$ be an algebraic closure of $F'$.
	Then $\sigma$ can be extended to an isomorphism $\tau$ of $E$ onto $\bar{F}'$ such that $\tau(a) = \sigma(a),\ \forall a \in F$.
\end{theorem}
\begin{proof}
	\textbf{Step 1 : Poset $S$}\\
	Let $E$ be an algebraic extension of $F$.
	Let $\sigma : F \to F'$ be an isomorphism.
	Let $S$ be the set of all pairs $(L,\lambda)$ such that $F \le L \le E$ and $\lambda$ is an extension of $\sigma$ onto a subfield of $\bar{F}$.
	$S$ is non-empty, since $(F,\sigma) \in S$.\\

	Consider the relation $\le$ on $S$ defined by $(L_1,\lambda_1) \le (L_2,\lambda_2)$ if $L_1 \le L_2$ and $\lambda_1(a) = \lambda_2(a),\ \forall a \in L_1$.
	Then $\le$ is a partial order on $S$ since $\le$ is reflexive, antisymmetric and transitive.
	\begin{commentary}
	\begin{enumerate}
		\item Reflexive\\
		Let $(L,\lambda) \in S$.
		Then $L \le L$ and $\lambda(a) = \lambda(a),\ \forall a \in L$.
		\item Anti-symmetric\\
		Let $(L_1,\lambda_1), (L_2,\lambda_2) \in S$.
		Suppose $(L_1,\lambda_1) \le (L_2,\lambda_2)$ where $L_1 \not\simeq L_2$.
		Then, $F \le L_1 < L_2 \le E$.
		Thus, $(L_2,\lambda_2) \not\le (L_1,\lambda_1)$.
		\item Transitive\\
		Let $(L_1,\lambda_1) \le (L_2,\lambda_2)$ and $(L_2,\lambda_2) \le (L_3,\lambda_3)$.
		Then, $F \le L_1 \le L_2 \le L_3 \le E$.
		And $\lambda_3(a) = \lambda_2(a) = \lambda_1(a), \forall a \in L_1 \subseteq L_2$.\\
		Thus, $(L_1,\lambda_1) \le (L_3,\lambda_3)$.
	\end{enumerate}
	\end{commentary}

	\textbf{Step 2 : Every chain in $S$ has an upper bound $(H,\lambda)$}\\
	Let $\{ (H_i,\lambda_i) : i \in I \}$ be a chain in $S$.
	Define $\displaystyle H = \cup \{H_i : i \in I\}$.
	We know that, if $c \in H$, then $c \in H_i$ for some $i \in I$.
	Define $\lambda$ from $H$ onto a subfield of $\bar{F}'$ such that $\lambda(c) = \lambda_i(c)$ where $ c \in H_i$.\\

	We need to prove that$\lambda$ is an isomorphism.
	Let $a,b \in H$.
	Then $a \in H_i$ and $b \in H_j$ for some $i,j \in I$.
	Then $H_i \le H_j$ or $H_j \le H_i$ since $H_i,H_j$ belongs to a chain.
	Suppose $H_j \le H_i$, then $a,b \in H_i$.
	Thus, $a+b,ab \in H_i$.
	And, $\lambda_i$ is an isomorphism on $H_i$.
	Thus,
	\[ \lambda(a+b) = \lambda_i(a + b) = \lambda_i(a) + \lambda_i(b) = \lambda(a) + \lambda(b) \]
	Similarly,
	\[ \lambda(ab) = \lambda_i(ab) = \lambda_i(a)\lambda_i(b) = \lambda(a)\lambda(b) \]
	If $\lambda(c) = 0$, then $\lambda_i(c) = 0$ for some $i \in I$.
	Since $\lambda_i$ is an isomorphism on $H_i$, $c = 0$.
	Therefore, $\lambda(c) = 0 \iff c = 0$.
	Clearly, $\lambda$ is an isomorphism.\\

	From the defintion of $H$ and $\lambda$, $(H,\lambda)$ is an upper bounded for the chain since $H_i \le H$ and $\lambda(c) = \lambda_i(c),\ \forall c \in H_i$.\\

	\textbf{Step 3 : $(K,\tau)$ is maximal, but $K \ne E$}\\
	We have shown that, every chain in $S$ has an upper bouned.
	By Zorn's lemma, $S$ must have a maximal element, say $(K,\tau)$.\\

	Suppose $K \ne E$.
	Let $\alpha \in E$ such that $\alpha \notin K$.
	Then $\alpha$ is algebraic over $K$ with $p(x) = irr(\alpha,K)$.
	Let $\psi_\alpha$ be the canonical isomorphism corresponding to the evaluation homomorphism $\phi_\alpha$.
	\[ \psi_\alpha : K[x]/\generator{p(x)} \to K(\alpha),\quad \phi_\alpha : K[x] \to K(\alpha) \]
	Consider the isomorphism $\tau : K \to K'$.
	Let $p(x) = a_0 + a_1 x + \dots + a_nx^n$.
	Then, $q(x) = \tau(p)(x) = \tau(a_0) + \tau(a_1) x + \dots + \tau(a_n)x^n$ is an irreducible polynomial over $K'$.\\

	Let $\alpha'$ be a zero of $q(x) \in K'[x]$.
	Consider $\psi_{\alpha'} : K'[x]/\generator{q(x)} \to K'(\alpha')$ which is analogous to $\psi_\alpha$.
	Let $\bar{\tau} : K[x]/\generator{p(x)} \to K'[x]/\generator{q(x)}$ be an extension of $\tau$ such that $x+\generator{p(x)} \to x+\generator{q(x)}$.
	Then $\psi_{\alpha'} \circ \bar{\tau} \circ \psi_\alpha^{-1} : K(\alpha) \to K'(\alpha')$ is an isomorphism.
	Clearly, $(K,\tau) \leq \left(K(\alpha),\psi_{\alpha'} \circ \bar{\tau} \circ \psi_{\alpha}^{-1}\right)$ which contradicts $(K,\tau)$ being a maximal element of $S$.
	Therefore, $K = E$ and $\tau : K \to K'$ is an extension of $\sigma : F \to F'$ where $F' \le K' \le \bar{F}'$.
\end{proof}

\begin{corollary}
	If $E \le \bar{F}$ is an algebraic extension of $F$ and $\alpha,\beta \in E$ are conjugates over $F$.
	Then the conjugate isomorphism $\psi_{\alpha,\beta} : F(\alpha) \to F(\beta)$ can be extended to an isomorphism of $E$ onto $\bar{F}$.
\end{corollary}
\begin{proof}
	Consider the conjugate isomorphism $\psi_{\alpha,\beta} : F(\alpha) \to F(\beta)$.
	Let $E$ be an algebraic extension of $F(\alpha)$.
	Then, by isomorphims extension theorem $\psi_{\alpha,\beta}$ can be extended to an isomorphism from $E$ onto a subfield of $\bar{F}'$.
\end{proof}

\begin{corollary}
	Let $\bar{F}$ and $\bar{F}'$ be two algebraic closure of $F$.
	Then $\bar{F}$ is isomorphic to $\bar{F}'$ under an isomorphism leaving each element of $F$ fixed.
\end{corollary}
\begin{proof}
	Let $i : F \to F$ be the identity isomorphism.
	Let $\bar{F}, \bar{F}'$, both be algebraic closures of $F$.
	By isomorphism extension theorem, $i$ can be extended to an isomorphism $\tau$ from the algebraic extension $\bar{F}$ onto a subfield of $\bar{F}'$ leaving $F$ fixed since $i(a) = a,\ \forall a \in F$.\\

	Since, $\tau$ is an isomorphism the range of $\tau$, $\tau[\bar{F}]$ is a subfield of $\bar{F}'$.
	We have, $\tau^{-1} : \tau[\bar{F}] \to \bar{F}$ is also an isomorphism onto $\bar{F}$.
	Again by isomorphism extension theorem, $\tau$ can be extended to an algebraic extension $\bar{F}'$ onto $\bar{F}$.
	However, $\tau^{-1}$ is already onto $\bar{F}$.
	Thus, $\tau : \bar{F} \to \bar{F}'$ is an isomorphism leaving $F$ fixed.
\end{proof}
\begin{important}
	In other words, for any field $F$, its algebraic closure $\bar{F}$ is unique upto an isomorphism leaving $F$ fixed.
\end{important}

\subsection{Index of field extension}
\begin{theorem}
	Let $E$ be a finite extension of $F$.
	Let $\sigma$ be an isomorphism of $F$ onto $F'$.
	Let $\bar{F}'$ be an algebraic closure of $F'$.
	Then, the number of extensions of $\sigma$ to an isomorphism of $E$ onto a subfield of $\bar{F}'$ is finite and is independent of $F',\bar{F}',\sigma$.
\end{theorem}
\begin{important}
	In other words, the number of extensions depends only on $F$ and $E$.
\end{important}
\begin{proof}
	\textbf{Step 1 : Index of extension of $F$ is independent of $F_1$}\\
	Let $\sigma_1 : F \to F_1$ and $\sigma_2 : F \to F_2$ be two isomorphisms.
	Let $E$ be an algebraic extension of $F$.
	And $\tau_1 : E \to \tau_1[E]$ and $\tau_2 : E \to \tau_2[E]$ be the extensions of $\sigma_1,\sigma_2$ from $E$ to subfields $\tau_1[E] \le \bar{F}_1$ and $\tau_2[E] \le \bar{F}_2$ respectively.
	Then $\tau_2 \circ \tau_1^{-1} : \tau_1[E] \to \tau_2[E]$ is an isomorphism.\\

	Let $\lambda$ be the extension of $\tau_2 \circ \tau_1^{-1}$ where $\lambda : \bar{F}_1 \to \bar{F}_2$.
	Now, we have $\lambda : \bar{F}_1 \to \bar{F}_2$ such that for any isomorphism extension $\tau_1$ from $E$ onto a subfield of $\bar{F}_1$, we have an isomorphism extension $\tau_2$ from $E$ on to $\bar{F}_2$ is given by $\tau_2 = \lambda\tau_1$.
	Thus, the number of extensions of $\sigma : F \to F'$ is independent of the choice of $\sigma$ and $F'$ (and $\bar{F}'$).\\

	\textbf{Step 2 : Number of possible extensions is finite}\\
	Let $\sigma : F \to F'$ be an isomorphism.
	Let $E$ be an algebraic extension of $F$.
	Let $\tau$ be an isomorphism extension of $\sigma$ to $E$ leaving $F$ fixed.
	Then, $E = F(\alpha_1,\alpha_2,\dots,\alpha_n)$ since every algebraic extensions is a finite extension.\\

	We know that, isomorphisms preserve irreducibility.
	\dag\footnote{Let $p(x)$ be irreducible over $F$.
	Let $\sigma : F \to F'$ be an isomorphism.
	Then there exists a polynomial $q(x)$ which is irreducible over $F'$.
	And if $p(x) = a_0 + a_1 x + \dots +a_nx^n$, then $q(x) = \sigma(a_0) + \sigma(a_1)x +\dots + \sigma(a_n)x^n$.
	We may write $q = \sigma_x(p)$ where $\sigma_x : F[x] \to F'[x]$.}\\
	Let $irr(\alpha_j,F) = p(x) \in F[x]$ with $\deg(\alpha_j,F) = k$.
	Then, 
	\[ p(x) = a_0 + a_1 x + \dots + a_k x^k \]
	We have, $\phi_{\alpha_j}(p(x)) = p(\alpha_j) = 0$.
	Let $q(x) \in F'[x]$ such that 
	\[ q(x) = \sigma_x(p)(x) = \sigma(a_0) + \sigma(a_1) x + \dots + \sigma(a_k) x^k \]
	Then, $\tau$ must map $\alpha_j$ to a zero of $q(x)$, say $\alpha_j'$ such that $\sigma(p(\alpha_j)) = 0 = q(\alpha_j')$.\\

	That is, for any isomorphism extension $\tau : E \to \bar{F}'$, we have $\tau(\alpha_j)$ is a zero of $q(x) \in F'[x]$.
	Clearly, any extension of $\sigma$ will have to map $\alpha_j$ to a zero of $q(x) \in F'[x]$.
	However, $q(x)$ has at most $k$ zeroes in $\bar{F}'$.\\

	Therefore, the number of extension of $\sigma$ is finite as $E$ is a finite extension ( number of $\alpha_j$s is finite ) and for each $\alpha_j$ the number of possible candidates $\tau(\alpha_j)$ in $\bar{F}'$ is finite.
	Thus, the number of possible extensions of an isomorphism $\sigma$ to an algebraic extension $E$ leaving $F$ fixed, is finite.
\end{proof}

\begin{definition}[index]
	Let $E$ be an extension of $F$.
	The index of $E$ over $F$, $\{E:F\}$ is the number of isomorphisms of $E$ onto a subfield of $\bar{F}$ leaving $F$ fixed.
\end{definition}

\begin{corollary}
	If $F \le E \le K$, where $K$ is a finite extension of $F$.
	Then $\{ K : F \} = \{ K : E \} \{ E : F \}$.
\end{corollary}
\begin{proof}
	Let $E$ be an algebraic extension of $F$ and $K$ be an algebraic extension of $E$.
	Then $K$ is an algebraic extension of $F$.\\

	We know that, the number of isomorphisms from $E$ onto a subfield of $\bar{F}$ leaving $F$ fixed, $\{ E : F \}$ is finite.
	Now, each of those isomorphisms have $\{ K : E \}$ extensions, since there are $\{ K : E \}$ different isomorphisms from $K$ onto a subfield of $\bar{F}$ leaving $E$ fixed.
	Therefore, there are $\{ K : E \}\{ E : F\}$ isomorphisms from $K$ onto a subfield of $\bar{F}$ leaving $F$ fixed.
	That is,
	\[ \{ K : F \} = \{ K : E \} \{ E : F \} \]
\end{proof}
For example, $\mathbb{Q}(\sqrt{2},\sqrt{3})$ has $4$ different isomorphisms onto a subfield of $\mathbb{C}$.
\[ \left\{ \mathbb{Q}(\sqrt{2},\sqrt{3}) : \mathbb{Q} \right\} = \left\{ \mathbb{Q}(\sqrt{2})(\sqrt{3}) : \mathbb{Q}(\sqrt{2}) \right\} \left\{ \mathbb{Q}(\sqrt{2}) : \mathbb{Q}\right\} \]
We have, $\mathbb{Q}(\sqrt{2},\sqrt{3}) = \mathbb{Q}(\sqrt{2})(\sqrt{3})$ and 
\[ \left\{\mathbb{Q}(\sqrt{2})(\sqrt{3}) : \mathbb{Q}(\sqrt{2}) \right\} = \left[ \mathbb{Q}(\sqrt{2})(\sqrt{3}) : \mathbb{Q}(\sqrt{2})\right] = \deg\left(\sqrt{3},\mathbb{Q}(\sqrt{2})\right) = 2 \]
\[ \left\{\mathbb{Q}(\sqrt{2}) : \mathbb{Q} \right\} = \left[ \mathbb{Q}(\sqrt{2}) : \mathbb{Q} \right] = \deg\left(\sqrt{2},\mathbb{Q}\right) = 2 \]

\subsection{Exercise \S49}
\begin{enumerate}
	\item
\end{enumerate}

\section{Splitting Fields \S50}
\begin{definition}[splitting field]
	Let $F$ be a field with algebraic closure $\bar{F}$.
	Let $\mathscr{F} = \{ f_i(x) \in F[x] : i \in I \}$ be a collection of polynomials over $F$.
	Then $E \le \bar{F}$ is a splitting field of $\mathscr{F}$ over $F$ if $E$ is the smallest subfield of $\bar{F}$ containing $F$ and all the zeroes of polynomials in $\mathscr{F}$.
\end{definition}
For example, $\mathbb{Q}(\sqrt{2},\sqrt{3})$ is the splitting field of $\{ x^2-2,x^2-3 \}$ over $\mathbb{Q}$.

\begin{theorem}
	Let $F \le E \le \bar{F}$.
	Then $E$ is a splitting field of $F$ if and only if every automorphism of $\bar{F}$ leaving $F$ fixed maps $E$ onto itself.
	And thus induces an automorphism of $E$ leaving $F$ fixed.
\end{theorem}
\begin{proof}
	Let $E$ be a splitting field of $F$ in $\bar{F}$ of $\{ f_i(x) : i \in I \}$.
	Let $\sigma$ be an automorphism of $\bar{F}$ leaving $F$ fixed.\\

	\textbf{Step 1 : $\{ \alpha_j : j \in J \}$ generates $E$}\\
	Let $\{ \alpha_j : j \in J\}$ be the set of all zeroes of $\mathscr{F} = \{ f_i(x) : i \in I\}$.
	We know that, the elements of  $F(\alpha_j)$ are of the form
	\[ \phi_{\alpha_j} g(x) = g(\alpha_j) =  a_0 + a_1 \alpha_j + \dots + a_{n_j-1}\alpha^{n_j-1} \]
	where $a_k \in F$, $\deg(\alpha_j,F) = n_j$.
	Clearly, $g(x)$ is some polynomial in $F[x]$ of degree less than $n_j$.\\

	Let $S$ be the set of all finite sums of finite products of elemenets of the form $g(\alpha_j)$.
	Clearly, $S \subset E$ and $S$ is closed under addition, closed under multiplication, contains identities ($0, 1 \in S$) and additive inverses of its elements.\\

	Let $\beta \in S$.
	Then $\beta$ is a finite sum of finite products of elements of the form $g(\alpha_{j_k})$.
	Then, an element $\beta \in S$ belongs to some $F(\alpha_{j_1},\alpha_{j_2},\dots,\alpha_{j_r}) \subset S$.
	Thus, $S$ has multiplicative inverse of each of its non-zero elements.
	Clearly, $S$ is a subfield of $E$ containing $F$ and $\alpha_j$s.
	That is, $S$ is the splitting field of $F$ containing all zeroes of $\mathscr{F}$.
	Therefore, $S = E$.
	In other words, $\{ \alpha_j : j \in J \}$ generates $E$ over $F$.
	\dag\footnote{$E$ is a vector space over the field $F$ spanned by $\{ \alpha_j : j \in J \}$. 
	Let $\beta \in E$.
	Then, $\beta = a_0 \alpha_0 + a_1 \alpha_1 + \dots + a_r \alpha_r$ where $a_k \in F$.}\\

	\textbf{Step 2 : $\sigma$ is an automorphism of $E$}\\
	Since $\{ \alpha_j : j \in J \}$ spans $E$ over $F$, $\sigma : \bar{F} \to \bar{F}$ is completely determined on $E$ by the images of $\alpha_j$s, say $\sigma(\alpha_j)$.
	And $\sigma(\alpha_j)$ is a zero of $irr(\alpha_j,F)$.
	If $f_i(\alpha_j) = 0$, then $irr(\alpha_j,F)$ divides $f_i(x)$.
	Similarly $irr(\sigma(\alpha_j),F)$ divides $f_i(x)$.
	Thus, $\sigma$ maps $E$ onto a subfield of $E$ isomorphically.
	Similarly, $\sigma^{-1}$ maps $E$ onto a subfield of $E$ isomorphically.
	Therefore, $\sigma$ is an automorphism on $E$.\\

	\textbf{Converse Part}\\

\end{proof}

\begin{definition}
	Let $E$ be an extension field of $F$.
	A polynomial $f(x) \in F[x]$ splits in $E[x]$ if it factors into linear components in $E[x]$.
\end{definition}
For example, $x^4-5x^2+6 \in \mathbb{Q}$ splits in $\mathbb{Q}(\sqrt{2},\sqrt{3})$ since 
\[ x^4-5x^2+6 = (x-\sqrt{2})(x+\sqrt{2})(x-\sqrt{3})(x+\sqrt{3}) \]

\begin{corollary}
	If $E \le \bar{F}$ is a splitting field over $F$, then every irreducible polynomial in $F[x]$ having a zero in $E$ splits in $E$.
\end{corollary}
\begin{proof}
\end{proof}

\begin{corollary}
	If $E \le \bar{F}$ is a splitting field over $F$, then every isomorphic mapping of $E$ onto a subfield of $\bar{F}$ leaving $F$ fixed is an automorphism of $E$.
	In particular, if $E$ is splitting field of finite degree over $F$, then
	\[ \{ E : F \} = |G(E/F)| \]
\end{corollary}
\begin{proof}
\end{proof}
\subsection{Exercise \S50}
\begin{enumerate}
	\item
\end{enumerate}

%Module 4
\pagebreak
{\Large Module 4 Galois Theory}
\section{Separable Extensions \S51}
\subsection{Multplicities of zeroes of a polynomial}
\subsection{Separable extensions}
\subsection{Perfect fields}
\subsection{The primitive element theorem}
\subsection{Exercise \S51}
\begin{enumerate}
	\item
\end{enumerate}

%\section{Automorphisms and Galois Theory \S52}
\section{Galois Theory \S53}
\subsection{Context}
\subsection{Normal extensions}
\subsection{The main theorem}
\subsection{Galois groups over finite fields}
\subsection{Exercise \S53}
\begin{enumerate}
	\item
\end{enumerate}

\section{Illustrations of Galois Theory \S54}
\subsection{Symmetric functions}
\subsection{Exercise \S54}
\begin{enumerate}
	\item
\end{enumerate}

\section{Cyclotomic Extensions \S55}
\subsection{The Galois group of a cyclotomic extension}
\subsection{Constructible polygons}
\subsection{Exercise \S54}
\begin{enumerate}
	\item
\end{enumerate}

\section{Insolvability of the quintic}
\begin{important}
	There exists polynomials of degree $5$ in $\mathbb{Q}[x]$ that are not solvable by radicals in $\mathbb{Q}$.
\end{important}
